### 2020-11-23 tex/ms.tex
reorg

\documentclass[modern]{aastex62}

% Load the corTeX style definitions
\input{cortex}

% Load custom style
\input{style}

% Bibliography
\bibliographystyle{aasjournal}

\usepackage{etoolbox}
\makeatletter % we need to patch \env@cases that has @ in its name
\patchcmd{\env@cases}{\quad}{\qquad\qquad}{}{}
\makeatother

\usepackage{enumitem}

% Begin!
\begin{document}

% Title
\title{%
    \textbf{
        Normalized Gaussian Processes
    }
}

\author{Rodrigo Luger}

\section{The problem}

Let $\mathbf{x} = \left( x_0 \,\, \cdots \,\, x_{K-1} \right)^\top$
be a $K$-dimensional multivariate normal random variable distributed
according to a Gaussian Process with mean $\pmb{\mu}$
and covariance $\pmb{\Sigma}$:
%
\begin{align}
    \mathbf{x} \sim \mathcal{N}\left( \pmb{\mu}, \pmb{\Sigma} \right)
    \quad.
\end{align}
%
For simplicity, let us assume the mean is constant, i.e.,
%
\begin{align}
    \pmb{\mu} = \mu \, \mathbf{j}_K
\end{align}
%
where $\mathbf{j}_K$ is the vector of $K$ ones.
%
Now suppose we cannot observe samples of $\mathbf{x}$ directly, but instead we can
observe samples from the \emph{normalized} process, which we will call
$\tilde{\mathbf{x}}$:
%
\begin{align}
    \tilde{\mathbf{x}}
     & \equiv \frac{\mathbf{x}}{\bar{x}}
    \nonumber                                                      \\[0.5em]
     & = \frac{\mathbf{x}}{\frac{1}{K}\sum\limits_{k=0}^{K-1} x_k}
    \quad.
\end{align}
%
The random variable $\tilde{\mathbf{x}}$ is no longer normally distributed, but as long as
the variance of $\bar{x}$ is small, we can approximate it as such. Let the mean
and covariance of $\tilde{\mathbf{x}}$ be $\tilde{\pmb{\mu}}$ and $\tilde{\pmb{\Sigma}}$, respectively:
%
\begin{align}
    \tilde{\mathbf{x}} \mathrel{\dot\sim} \mathcal{N}\left( \tilde{\pmb{\mu}}, \tilde{\pmb{\Sigma}} \right)
    \quad.
\end{align}
%
By definition, the mean is unity, i.e,
%
\begin{align}
    \tilde{\pmb{\mu}} = \mathbf{j}_K
    \quad.
\end{align}
%
What is the expression for $\tilde{\pmb{\Sigma}}$?

\section{The solution}

The covariance is given by
%
\begin{align}
    \tilde{\pmb{\Sigma}}
     & =
    \mathbb{E}\big[ \tilde{\mathbf{x}} \tilde{\mathbf{x}}^\top \big]
    - \tilde{\pmb{\mu}}\tilde{\pmb{\mu}}^\top
    \nonumber \\[0.5em]
     & =
    \mathbb{E}\left[ \frac{\mathbf{x}\mathbf{x}^\top}{\bar{x}^2} \right]
    - \mathbf{J}_K
    \quad,
\end{align}
%
where $\mathbf{J}_K = \mathbf{j}_K \mathbf{j}_K^\top$ is the $K\times K$ matrix of ones.
To evaluate this, it is convenient to write
%
\begin{align}
    \mathbf{x} = \pmb{\mu} + \mathbf{L} \mathbf{u}
    \quad,
\end{align}
%
where $\mathbf{L}$ is the lower Cholesky decomposition of $\pmb{\Sigma}$,
i.e.,
%
\begin{align}
    \pmb{\Sigma} = \mathbf{L}\,\mathbf{L}^\top
\end{align}
%
and $\mathbf{u}$ is a standard multivariate normal random variable,
%
\begin{align}
    \mathbf{u} \sim \mathcal{N}\left( 0, \mathbf{I}_K \right)
    \quad,
\end{align}
%
where $\mathbf{I}_K$ is the
$K \times K$ identity matrix.
The expression for the covariance $\tilde{\pmb{\Sigma}}$ may now be written
%
\begin{align}
    \tilde{\pmb{\Sigma}}
     & =
    \mathbb{E}\left[
        \frac{
            (\pmb{\mu} + \mathbf{L} \mathbf{u})(\pmb{\mu} + \mathbf{L} \mathbf{u})^\top
        }{
            \bar{x}^2
        }
        \right]
    - \mathbf{J}_K
\end{align}
%
The mean $\bar{x}$ is
%
\begin{align}
    \bar{x} & = \sum\limits_{j=0}^{K-1}(\mu_j + L_{i,j}u_j)
    \nonumber                                               \\
            & =
    \mu + \frac{1}{K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}
    \quad.
\end{align}
%
Plugging this in and dividing the numerator and denominator in the expecation
by $\mu^2$, we obtain
%
\begin{align}
    \tilde{\pmb{\Sigma}}
     & =
    \frac{1}{\mu^2}
    \mathbb{E}\left[
        \frac{
            (\pmb{\mu} + \mathbf{L} \mathbf{u})(\pmb{\mu} + \mathbf{L} \mathbf{u})^\top
        }{
            \left(1 + \frac{1}{\mu K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^2
        }
        \right]
    - \mathbf{J}_K
    \nonumber \\[0.5em]
     & =
    \frac{1}{\mu^2}
    \mathbb{E}\left[
        \frac{
            \mu^2 \mathbf{J}_K
            +
            \mu \, \mathbf{j}_K\mathbf{u}^\top \mathbf{L}^\top
            +
            \mu \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top
            +
            \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top
        }{
            \left(1 + \frac{1}{\mu K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^2
        }
        \right]
    - \mathbf{J}_K
    \quad.
\end{align}
%
The denominator in the expression above makes direct evaluation of the expectation
intractable. As long as
$\big| \frac{1}{\mu K}\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u} \big| < 1$, we
can Taylor expand the covariance as
%
\begin{align}
    \label{eq:SigmaTildeExp}
    \tilde{\pmb{\Sigma}}
     & =
    \frac{1}{\mu^2}
    \mathbb{E}\left[
        \Bigg(
        \mu^2 \mathbf{J}_K
        +
        \mu \, \mathbf{j}_K\mathbf{u}^\top \mathbf{L}^\top
        +
        \mu \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top
        +
        \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top
        \Bigg)
        \left(
        \sum\limits_{n=0}^\infty
        (-1)^n (n + 1) z^n
        \right)
        \right]
    - \mathbf{J}_K
    \quad,
\end{align}
%
where we define the scalar quantity
%
\begin{align}
    z \equiv \frac{1}{\mu K}\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}
    \quad.
\end{align}
%
In the Appendix, we show that this expression may be written as
the infinite series
%
\begin{align}
    \tilde{\pmb{\Sigma}}
     & =
    \frac{1}{\mu^2} \pmb{\Sigma}
    +
    \sum\limits_{n=1}^\infty
    \frac{(-1)^n(n + 1)}{\mu^{n + 2}}
    \,
    \pmb{\Lambda}_n
    \quad.
\end{align}
%
where we define
%
\begin{align}
    \pmb{\Lambda}_n
     & \equiv
    g_n \, \bar{\Sigma}^\frac{n}{2} \, (\pmb{\Sigma} + \mu^2\mathbf{J}_K)
    \, +
    K g_{n+1} \mu  \,
    \left(
    \mathbf{S}^\frac{n + 1}{2}
    +
    {\mathbf{S}^\top}^\frac{n + 1}{2}
    \right)
    \, +
    n g_n \, \mathbf{S}^\frac{n}{2}\pmb{\Sigma}
\end{align}
%
and
%
\begin{align}
    \mathbf{S}
     & \equiv
    \frac{1}{K^2} \pmb{\Sigma} \, \mathbf{J}_K
\end{align}
%
where $\bar{\Sigma}$ is the average of all the elements in $\pmb{\Sigma}$ and
%
\begin{align}
    g_n
     & =
    \begin{cases}
        \dfrac{n!}{2^\frac{n}{2} \left(\frac{n}{2}\right)!} & n \, \mathrm{even}
        \\
        0                                                   & n \, \mathrm{odd}
        \quad.
    \end{cases}
\end{align}
%
The convergence criterion for this series may be written
%
\begin{align}
    \pmb{E}\big[|z|\big] < 1
\end{align}
%
or, equivalently,
%
\begin{align}
    \pmb{E}\big[z^2\big] &< 1
    \nonumber \\
    \frac{\bar{\Sigma}}{\mu^2} &< 1
    \quad.
\end{align}
%

\clearpage

\appendix

\section{Computing $\tilde{\pmb{\Sigma}}$}
%
Since the expectation is a linear operator, we can write Equation~(\ref{eq:SigmaTildeExp})
as
%
\begin{align}
    \tilde{\pmb{\Sigma}}
     & =
    \frac{1}{\mu^2}
    \sum\limits_{n=0}^\infty
    (-1)^n (n + 1)
    \,
    \mathbb{E}\left[
        z^n
        \Bigg(
        \mu^2 \mathbf{J}_K
        +
        \mu \, \mathbf{j}_K\mathbf{u}^\top \mathbf{L}^\top
        +
        \mu \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top
        +
        \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top
        \Bigg)
        \right]
    - \mathbf{J}_K
    \nonumber \\[0.5em]
     & =
    \sum\limits_{n=0}^\infty
    \frac{(-1)^n}{\mu^{2 + n}}
    \,
    \left(
    \mu^2 \mathbf{P}_n
    +
    \mu \, \mathbf{Q}_n
    +
    \mu \, \mathbf{Q}_n^\top
    +
    \mathbf{R}_n
    \right)
    - \mathbf{J}_K
    \quad,
\end{align}
%
where we define the matrices
%
\begin{align}
    \mathbf{P}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{J}_K \right]
    \nonumber                                                                                                                                                                                  \\[0.5em]
    \mathbf{Q}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top \right]
    \nonumber                                                                                                                                                                                  \\[0.5em]
    \mathbf{R}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top \right]
    \quad.
\end{align}
%
In order to compute these matrices,
we will make use of the expression for the
$n^\mathrm{th}$ moment of the standard normal distribution:
%
\begin{align}
    \mathbb{E}\left[ u^n \right] & = g_n
\end{align}
%
for scalar $u \sim \mathcal{N}(0, 1)$, where
%
\begin{align}
    g_n
     & =
    \begin{cases}
        \dfrac{n!}{2^\frac{n}{2} \left(\frac{n}{2}\right)!} & n \, \mathrm{even}
        \\
        0                                                   & n \, \mathrm{odd}
        \quad.
    \end{cases}
\end{align}
%
\citep[e.g.,][]{Winkelbauer2012}.
We can apply this relation to compute expectations
of products of the components of a random standard normal vector $\mathbf{u}$:
%
\begin{align}
    \mathbb{E}\left[u_i \right]                    & = 0
    \\[1em]
    \mathbb{E}\left[u_i u_j\right]                 & = g_2
    \\[1em]
    \mathbb{E}\left[u_i u_j u_k\right]             & = 0
    \\[1em]
    \mathbb{E}\left[u_i u_j u_k u_l\right]         & =
    g_4 \, \delta_{i, j} \delta_{k, l} \, \delta_{i, k}
    +
    g_2^2 \left(
    \delta_{i, j} \, \delta_{k, l} \, \bar{\delta}_{i, k}
    +
    \delta_{i, k} \, \delta_{j, l} \, \bar{\delta}_{i, j}
    +
    \delta_{i, l} \, \delta_{j, k} \, \bar{\delta}_{i, j}
    \right)
    \\[1em]
    \mathbb{E}\left[u_i u_j u_k u_l u_m\right]     & = 0
    \\[1em]
    \mathbb{E}\left[u_i u_j u_k u_l u_m u_n\right] & =
    ...
    \quad,
\end{align}
%
where $\delta$ is the Kronecker delta and $\bar{\delta} \equiv 1 - \delta$.

\subsection{The $\mathbf{P}$ expectation}

Let us begin by computing the first several terms in $\mathbf{P}$.
%
\begin{align}
    \mathbf{P}_0 & = \mathbb{E}\left[ \mathbf{J}_K \right]
    \nonumber                                              \\
                 & = \mathbf{J}_K
\end{align}
%
since $\mathbf{J}_K$ is constant. Next,
%
\begin{align}
    \mathbf{P}_1 & = \frac{2}{K}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{J}_K \right]
    \nonumber                                                                                                                 \\
                 & = \frac{2}{K}\left(\mathbf{j}_K^\top \mathbf{L} \, \mathbb{E}\left[ \mathbf{u} \right]\right) \mathbf{J}_K
    \nonumber                                                                                                                 \\
                 & = \mathbf{0}
\end{align}
%
since $\mathbb{E}\left[ \mathbf{u} \right] = \mathbf{0}$. The next term is
%
\begin{align}
    \mathbf{P}_2 & = \frac{3}{K^2}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^2 \mathbf{J}_K \right]
    \nonumber                                                                                                                                                                      \\
                 & = \frac{3}{K^2}\mathbb{E}\left[\left(\mathbf{j}_K^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j}_K \right)  \mathbf{J}_K \right]
    \nonumber                                                                                                                                                                      \\
                 & = \frac{3}{K^2}\left(\mathbf{j}_K^\top \mathbf{L} \, \mathbb{E}\left[ \mathbf{u} \mathbf{u}^\top \right] \mathbf{L}^\top \, \mathbf{j}_K \right)  \mathbf{J}_K
    \nonumber                                                                                                                                                                      \\
                 & = \frac{3}{K^2}\left(\mathbf{j}_K^\top \mathbf{L} \mathbf{L}^\top \, \mathbf{j}_K \right)  \mathbf{J}_K
    \nonumber                                                                                                                                                                      \\
                 & = \frac{3}{K^2}\mathrm{sum}(\mathbf{\Sigma}) \mathbf{J}_K
    \nonumber                                                                                                                                                                      \\
                 & = 3 \, \bar{\Sigma} \, \mathbf{J}_K
\end{align}
%
where $\bar{\Sigma}$ is the average of all entries in $\pmb{\Sigma}$ and
we made use of the fact that $\mathbb{E}\left[ \mathbf{u} \mathbf{u}^\top\right] = \mathbf{I}_K$.
%
Next,
%
\begin{align}
    \mathbf{P}_3 & = \frac{4}{K^3}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^3 \mathbf{J}_K \right]
    \nonumber                                                                                                                                                                                                                    \\
                 & = \frac{4}{K^3}\mathbb{E}\left[\left(\mathbf{j}_K^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j}_K \, \mathbf{j}_K^\top \mathbf{L} \,  \mathbf{u} \right) \mathbf{J}_K \right]
    \nonumber                                                                                                                                                                                                                    \\
                 & = \frac{4}{K^3}\left(\mathbf{j}_K^\top \mathbf{L} \,  \mathbb{E}\left[\mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{J}_K \mathbf{L} \,  \mathbf{u}\right] \right) \mathbf{J}_K
    \nonumber                                                                                                                                                                                                                    \\
                 & = \mathbf{0}
\end{align}
%
where we made use of the fact that we may write the component at index $i$ of the vector within the expectation in the next-to-last line
as
\begin{align}
    \mathbb{E}\left[\mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{J}_K \mathbf{L} \,  \mathbf{u}\right]_{i} = \sum\limits_{k,l}(\mathbf{L}^\top \mathbf{J}_K \mathbf{L})_{kl} u_i u_k u_l = 0
    \quad,
    \nonumber
\end{align}
%
which is zero since it is the product of an odd number of random normal variables.
Finally,
%
\begin{align}
    \mathbf{P}_4 & = \frac{5}{K^4}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^4 \mathbf{J}_K \right]
    \nonumber                                                                                                                                                                                                                                                                        \\
                 & = \frac{5}{K^4}\mathbb{E}\left[\left(\mathbf{j}_K^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j}_K \, \mathbf{j}_K^\top \mathbf{L} \,  \mathbf{u} \, \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j}_K \right) \mathbf{J}_K \right]
    \nonumber                                                                                                                                                                                                                                                                        \\
                 & = \frac{5}{K^4}\left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{E} \, \mathbf{L}^\top \, \mathbf{j}_K \right) \mathbf{J}_K
    \quad,
\end{align}
%
where we define
%
\begin{align}
    \mathbf{E} \equiv \mathbb{E}\left[ \mathbf{u} \mathbf{u}^\top  \mathbf{A} \,  \mathbf{u} \mathbf{u}^\top \right]
\end{align}
%
and
%
\begin{align}
    \mathbf{A} \equiv \mathbf{L}^\top \, \mathbf{J}_K \, \mathbf{L}
    \quad.
\end{align}
%
The components of this matrix are
%
\begin{align}
    E_{ij} & =
    \sum\limits_{k,l}A_{kl} \mathbb{E}(u_i u_j u_k u_l)
    \nonumber  \\
           & =
    \sum\limits_{k,l}A_{kl}
    \Big(
    g_4 \, \delta_{i, j} \, \delta_{k, l} \, \delta_{i, k}
    +
    g_2^2 \big(
        \delta_{i, j} \, \delta_{k, l} \, \bar{\delta}_{i, k}
        +
        \delta_{i, k} \, \delta_{j, l} \, \bar{\delta}_{i, j}
        +
        \delta_{i, l} \, \delta_{j, k} \, \bar{\delta}_{i, j}
        \big)
    \Big)
    \nonumber  \\
           & =
    2 A_{ij} + \sum\limits_k A_{kk}
    \quad,
\end{align}
%
where we used the fact that $\mathbf{A} = \mathbf{A}^\top$. We may thus write
%
\begin{align}
    \mathbf{E} & =
    2 \, \mathbf{A} + \mathrm{tr}(\mathbf{A}) \mathbf{I}_K
    \nonumber      \\
               & =
    2 \, \mathbf{L}^\top \, \mathbf{J}_K \, \mathbf{L} + \mathrm{sum}(\pmb{\Sigma}) \mathbf{I}_K
    \quad.
\end{align}
%
Inserting this back into the expression for $\mathbf{P}_4$, we obtain
%
\begin{align}
    \mathbf{P}_4 & =
    \frac{5}{K^4}
    \bigg(
    2 \, \big(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{L}^\top \, \mathbf{J}_K \, \mathbf{L} \, \mathbf{L}^\top \, \mathbf{j}_K \big)
    +
    \mathrm{sum}(\pmb{\Sigma}) \big(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{L}^\top \, \mathbf{j}_K \big)
    \bigg) \mathbf{J}_K
    \nonumber        \\
                 & =
    3 \, \bar{\Sigma}^2 \mathbf{J}_K
    \quad.
\end{align}
%
The general term in this sequence is
%
\begin{align}
    \mathbf{P}_n & =
    \mathbf{J}_K
    \begin{cases}
        0                                       & n \, \mathrm{odd}
        \\
        g_n (n + 1) \, \bar{\Sigma}^\frac{n}{2} & n \, \mathrm{even}
        \quad.
    \end{cases}
\end{align}
%

\subsection{The $\mathbf{Q}$ expectation}
%
Let us again compute the first several terms of this expectation matrix.
%
\begin{align}
    \mathbf{Q}_0 & = \mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top \right]
    \nonumber                                                                                                                                                  \\
                 & = \mathbf{L} \, \mathbb{E}\left[  \mathbf{u} \right] \, \mathbf{j}_K^\top
    \nonumber                                                                                                                                                  \\
                 & = \mathbf{0}
    %
    \\[1em]
    %
    \mathbf{Q}_1 & = \frac{1}{K}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top \right]
    \nonumber                                                                                                                                                  \\
                 & = \frac{1}{K}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{L} \, \mathbf{u} \right] \, \mathbf{j}_K^\top
    \nonumber                                                                                                                                                  \\
                 & = \frac{1}{K}\mathbb{E}\left[ \mathbf{L} \, \mathbf{u} (\mathbf{u}^\top \mathbf{L}^\top \mathbf{j}_K) \right] \, \mathbf{j}_K^\top
    \nonumber                                                                                                                                                  \\
                 & = \frac{1}{K}\mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \mathbf{u}^\top \mathbf{L}^\top  \right] \, \mathbf{J}_K
    \nonumber                                                                                                                                                  \\
                 & = \frac{1}{K}\mathbf{L} \, \mathbb{E}\left[  \mathbf{u} \mathbf{u}^\top   \right]  \, \mathbf{L}^\top \mathbf{J}_K
    \nonumber                                                                                                                                                  \\
                 & = \frac{1}{K}\mathbf{L} \, \mathbf{L}^\top \mathbf{J}_K
    \nonumber                                                                                                                                                  \\
                 & = \frac{1}{K}\pmb{\Sigma} \, \mathbf{J}_K
\end{align}
%
where we made liberal use of the fact that $\left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)$ is a scalar. Continuing,
%
\begin{align}
    \mathbf{Q}_2 & = \frac{2}{K^2}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^2 \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top \right]
    \nonumber                                                                                                                                                                                         \\
                 & =  \frac{2}{K^2}\mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \, (\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}) (\mathbf{u}^\top \mathbf{L}^\top \mathbf{j}_K) \mathbf{j}_K^\top \right]
    \nonumber                                                                                                                                                                                         \\
                 & = \frac{2}{K^2}\mathbf{L} \, \mathbb{E}\left[ \mathbf{u} \, \mathbf{j}_K^\top \mathbf{L} \, \mathbf{u} \mathbf{u}^\top \right] \, \mathbf{L}^\top \mathbf{J}_K
    \nonumber                                                                                                                                                                                         \\
                 & = \mathbf{0}
\end{align}
%
since again the components of the expectation in the next-to-last line involve products of three standard normal random variables.
Next,
\begin{align}
    \mathbf{Q}_3 & = \frac{3}{K^3}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^3 \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top \right]
    \nonumber                                                                                                                                                      \\
                 & = \xxx{...}
    \nonumber                                                                                                                                                      \\
                 & =
    \frac{3}{K^3}\mathbf{e} \, \mathbf{j}_K^\top
\end{align}
%
% 3 \, \pmb{\Sigma} \, \mathbf{J}_K \, \pmb{\Sigma} \, \mathbf{J}_K
%
where we define
%
\begin{align}
    \mathbf{e} \equiv \mathbb{E}\left[
        \left(
        \mathbf{v}^\top \mathbf{u} \mathbf{u}^\top \mathbf{v}
        \mathbf{v}^\top \mathbf{u}
        \right)
        \mathbf{L} \mathbf{u}
        \right]
\end{align}
%
and
%
\begin{align}
    \mathbf{v} \equiv \mathbf{L}^\top \, \mathbf{j}_K
    \quad.
\end{align}
%
The components of $\mathbf{e}$ are given by
%
\begin{align}
    e_{i} & =
    \sum\limits_{j,k,l,m}L_{ij} v_k v_l v_m \mathbb{E}(u_j u_k u_l u_m)
    \nonumber \\
          & =
    \sum\limits_{j,k,l,m}L_{ij} v_k v_l v_m
    \Big(
    g_4 \, \delta_{j, k} \, \delta_{l, m} \, \delta_{j, l}
    +
    g_2^2 \big(
        \delta_{j, k} \, \delta_{l, m} \, \bar{\delta}_{j, l}
        +
        \delta_{j, l} \, \delta_{k, m} \, \bar{\delta}_{j, k}
        +
        \delta_{j, m} \, \delta_{k, l} \, \bar{\delta}_{j, k}
        \big)
    \Big)
    \nonumber \\
          & =
    \xxx{...}
\end{align}
%
We may thus write
%
\begin{align}
    \mathbf{e} & = 3 \, \pmb{\Sigma} \, \mathbf{J}_K \, \pmb{\Sigma} \, \mathbf{j}_K
    \quad.
\end{align}
%
Inserting this back into the expression for $\mathbf{Q}_3$, we obtain
%
\begin{align}
    \mathbf{Q}_3 & =
    \frac{9}{K^3} \, (\pmb{\Sigma} \, \mathbf{J}_K)^2
\end{align}
%
Based on this pattern, the general term in $\mathbf{Q}$ is
%
\begin{align}
    \mathbf{Q}_n & =
    \begin{cases}
        \mathbf{0}                                                                   & n \, \mathrm{even}
        \\
        \frac{(n + 1)g_{n+1}}{K^n} \, (\pmb{\Sigma} \, \mathbf{J}_K)^\frac{n + 1}{2} & n \, \mathrm{odd}
        \quad.
    \end{cases}
\end{align}

\subsection{The $\mathbf{R}$ expectation}
%
The first several terms in $\mathbf{R}$ are given by
%
\setlength{\abovedisplayskip}{1em}
\begin{align}
    \mathbf{R}_0 & = \mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top \right]
    \nonumber                                                                                                                                                                \\
                 & = \mathbf{L} \, \mathbb{E}\left[  \mathbf{u} \, \mathbf{u}^\top \right] \, \mathbf{L}^\top
    \nonumber                                                                                                                                                                \\
                 & = \pmb{\Sigma}
    %
    \\[1em]
    %
    \mathbf{R}_1 & = \frac{1}{K}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top \right]
    \nonumber                                                                                                                                                                \\
                 & = \mathbf{0}
    %
\end{align}
%
since its elements are all products of three standard normal random variables. Next,
%
\begin{align}
    %
    \mathbf{R}_2 & = \mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^2 \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top \right]
    \nonumber                                                                                                                                                       \\
                 & = \xxx{...}
    \nonumber                                                                                                                                                       \\
                 & = 2 \pmb{\Sigma} \mathbf{J}_K \pmb{\Sigma} + \mathrm{sum}(\pmb{\Sigma}) \pmb{\Sigma}
\end{align}
%
\xxx{By trial and error, I found that}
%
\begin{align}
    %
    \mathbf{R}_4 & = \frac{5}{K^4}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^4 \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top \right]
    \nonumber                                                                                                                                                                    \\
                 & = \xxx{...}
    \nonumber                                                                                                                                                                    \\
                 & = \frac{5}{K^4} \Big( 12 (\pmb{\Sigma} \mathbf{J}_K)^2 \pmb{\Sigma} + 3 \, \mathrm{sum}(\pmb{\Sigma})^2 \pmb{\Sigma} \Big)
\end{align}
%
Based on this pattern, the general term in $\mathbf{R}$ is
%
\begin{align}
    \mathbf{R}_n & =
    \begin{cases}
        \mathbf{0}                                                                                                                                     & n \, \mathrm{odd}
        \\
        \frac{n (n + 1) g_{n}}{K^n} \, (\pmb{\Sigma} \, \mathbf{J}_K)^\frac{n}{2}\pmb{\Sigma} + (n + 1) g_{n} \, \bar{\Sigma}^\frac{n}{2} \pmb{\Sigma} & n \, \mathrm{even}
        \quad.
    \end{cases}
\end{align}

\subsection{The final result}
Inserting the matrices $\mathbf{P}$, $\mathbf{Q}$, and $\mathbf{R}$ into the expression
for $\tilde{\pmb{\Sigma}}$ and rearranging,
we obtain
%
\begin{align}
    \tilde{\pmb{\Sigma}}
     & =
    \frac{1}{\mu^2} \pmb{\Sigma}
    +
    \frac{1}{\mu^2}
    \sum\limits_{n=1}^\infty
    \frac{(-1)^n(n + 1)}{\mu^{n}}
    \,
    \bigg[
        g_n \, \bar{\Sigma}^\frac{n}{2} \, (\pmb{\Sigma} + \mu^2\mathbf{J}_K)
        \, +
        \nonumber                 \\[0.5em]
     & \phantom{XXXXXXXXXXXXXXX.}
    K g_{n+1} \mu  \,
    \left(
    \left(\pmb{\Sigma} \, \frac{\mathbf{J}_K}{K^2}\right)^\frac{n + 1}{2}
    +
    \left(\frac{\mathbf{J}_K}{K^2} \, \pmb{\Sigma}\right)^\frac{n + 1}{2}
    \right)
    \, +
    \nonumber                     \\[0.5em]
     & \phantom{XXXXXXXXXXXXXXX.}
    n g_n \, \left(\pmb{\Sigma} \, \frac{\mathbf{J}_K}{K^2}\right)^\frac{n}{2}\pmb{\Sigma}
    \bigg]
    \quad.
\end{align}

\bibliography{bib}
\end{document}

### 2020-11-24 tex/ms.tex
better

@@
      & =
-    \mathbb{E}\big[ \tilde{\mathbf{x}} \tilde{\mathbf{x}}^\top \big]
-    - \tilde{\pmb{\mu}}\tilde{\pmb{\mu}}^\top
+    \mathbb{E}\big[ (\tilde{\mathbf{x}} - \tilde{\pmb{\mu}}) (\tilde{\mathbf{x}} - \tilde{\pmb{\mu}} )^\top \big]
     \nonumber \\[0.5em]
      & =
-    \mathbb{E}\left[ \frac{\mathbf{x}\mathbf{x}^\top}{\bar{x}^2} \right]
-    - \mathbf{J}_K
+    \mathbb{E}\left[
+        \left(\frac{\mathbf{x}}{\bar{x}} - \mathbf{j}_K\right)
+        \left(\frac{\mathbf{x}}{\bar{x}} - \mathbf{j}_K\right)^\top
+        \right]
+    \nonumber \\[0.5em]
+     & =
+    \mathbb{E}\left[
+        \frac{\mathbf{x}\mathbf{x}^\top}{\bar{x}^2}
+        -
+        \frac{\mathbf{x}\,\mathbf{j}_K^\top}{\bar{x}}
+        -
+        \frac{\mathbf{j}\,\mathbf{x}_K^\top}{\bar{x}}
+        +
+        \mathbf{J}_K
+        \right]
+    \nonumber \\[0.5em]
+     & =
+    \mathbb{E}\left[
+        \frac{\mathbf{x}\mathbf{x}^\top}{\bar{x}^2}
+        \right]
+    -
+    \mathbb{E}\left[
+        \frac{\mathbf{x}\,\mathbf{j}_K^\top}{\bar{x}}
+        \right]
+    -
+    \mathbb{E}\left[
+        \frac{\mathbf{j}_K\,\mathbf{x}^\top}{\bar{x}}
+        \right]
+    +
+    \mathbf{J}_K
     \quad,
@@
         \right]
-    - \mathbf{J}_K
+    -
+    \mathbb{E}\left[
+        \frac{
+            (\pmb{\mu} + \mathbf{L} \mathbf{u})\mathbf{j}_K^\top
+        }{
+            \bar{x}
+        }
+        \right]
+    -
+    \mathbb{E}\left[
+        \frac{
+            \mathbf{j}_K(\pmb{\mu} + \mathbf{L} \mathbf{u})^\top
+        }{
+            \bar{x}
+        }
+        \right]
+    +
+    \mathbf{J}_K
 \end{align}
@@
             & =
-    \mu + \frac{1}{K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}
-    \quad.
-\end{align}
-%
-Plugging this in and dividing the numerator and denominator in the expecation
-by $\mu^2$, we obtain
-%
-\begin{align}
-    \tilde{\pmb{\Sigma}}
-     & =
-    \frac{1}{\mu^2}
-    \mathbb{E}\left[
-        \frac{
-            (\pmb{\mu} + \mathbf{L} \mathbf{u})(\pmb{\mu} + \mathbf{L} \mathbf{u})^\top
-        }{
-            \left(1 + \frac{1}{\mu K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^2
-        }
-        \right]
-    - \mathbf{J}_K
-    \nonumber \\[0.5em]
-     & =
-    \frac{1}{\mu^2}
-    \mathbb{E}\left[
-        \frac{
-            \mu^2 \mathbf{J}_K
-            +
-            \mu \, \mathbf{j}_K\mathbf{u}^\top \mathbf{L}^\top
-            +
-            \mu \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top
-            +
-            \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top
-        }{
-            \left(1 + \frac{1}{\mu K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^2
-        }
-        \right]
-    - \mathbf{J}_K
-    \quad.
-\end{align}
-%
-The denominator in the expression above makes direct evaluation of the expectation
-intractable. As long as
-$\big| \frac{1}{\mu K}\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u} \big| < 1$, we
-can Taylor expand the covariance as
-%
-\begin{align}
-    \label{eq:SigmaTildeExp}
-    \tilde{\pmb{\Sigma}}
-     & =
-    \frac{1}{\mu^2}
-    \mathbb{E}\left[
-        \Bigg(
-        \mu^2 \mathbf{J}_K
-        +
-        \mu \, \mathbf{j}_K\mathbf{u}^\top \mathbf{L}^\top
-        +
-        \mu \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top
-        +
-        \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top
-        \Bigg)
-        \left(
-        \sum\limits_{n=0}^\infty
-        (-1)^n (n + 1) z^n
-        \right)
-        \right]
-    - \mathbf{J}_K
+    \mu + \frac{1}{K}\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}
+    \nonumber                                               \\
+            & = \mu(1 + z)
     \quad,
@@
 %
-where we define the scalar quantity
+where we define the quantity
 %
@@
 %
-In the Appendix, we show that this expression may be written as
-the infinite series
+Plugging this in and rearranging, we obtain
 %
 \begin{align}
+    \label{eq:SigmaPQR}
     \tilde{\pmb{\Sigma}}
      & =
-    \frac{1}{\mu^2} \pmb{\Sigma}
+    \mathbf{P}
+    -
+    \frac{1}{\mu}
+    \left(
+    \mathbf{Q}
     +
-    \sum\limits_{n=1}^\infty
-    \frac{(-1)^n(n + 1)}{\mu^{n + 2}}
+    \mathbf{Q}^\top
+    \right)
+    +
+    \frac{1}{\mu^2}
+    \mathbf{R}
+    \quad,
+\end{align}
+%
+where we define the matrices
+%
+\begin{align}
+    %
+    \label{eq:Pexact}
+    \mathbf{P} & \equiv
+    \mathbb{E}\Big[
+        \frac{z^2 \, \mathbf{J}_K}{(1 + z)^2}
+        \Big]
+    %
+    \\[0.5em]
+    %
+    \label{eq:Qexact}
+    \mathbf{Q} & \equiv
+    \mathbb{E}\left[
+        \frac{z\, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top}{(1 + z)^2}
+        \right]
+    %
+    \\[0.5em]
+    %
+    \label{eq:Rexact}
+    \mathbf{R} & \equiv
+    \mathbb{E}\left[
+        \frac{ \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top}{(1 + z)^2}
+        \right]
+\end{align}
+%
+The denominator in the expressions above makes direct evaluation of the expectations
+intractable. As long as
+$\big|z| < 1$, we can Taylor expand the matrices as
+%
+\begin{align}
+    \mathbf{P}
+     & =
+    \sum\limits_{n=0}^\infty
+    (-1)^n (n + 1)
     \,
-    \pmb{\Lambda}_n
-    \quad.
+    \mathbb{E}\left[
+        z^{n + 2}
+        \,
+        \mathbf{J}_K
+        \right]
+    \\[0.5em]
+    \mathbf{Q}
+     & =
+    \sum\limits_{n=0}^\infty
+    (-1)^n (n + 1)
+    \,
+    \mathbb{E}\left[
+        z^{n + 1} \,
+        \mathbf{L}
+        \,
+        \mathbf{u}
+        \,
+        \mathbf{j}_K^\top
+        \right]
+    \\[0.5em]
+    \mathbf{R}
+     & =
+    \sum\limits_{n=0}^\infty
+    (-1)^n (n + 1)
+    \,
+    \mathbb{E}\left[
+        z^n \, \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top
+        \right]
+\end{align}
+%
+In the Appendix, we show that these may be computed from
+%
+\begin{align}
+    \mathbb{E}\left[
+        z^{n + 2} \, \mathbf{J}_K
+        \right]
+     & =
+    (n + 1) g_{n} \, \bar{\Sigma}^\frac{n+2}{2} \, \mathbf{J}_K
+    \\[0.5em]
+    \mathbb{E}\left[
+        z^{n + 1} \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top
+        \right]
+     & =
+    (n + 1) K \, g_{n} \, \mathbf{S}^\frac{n+2}{2}
+    \\[0.5em]
+    \mathbb{E}\left[
+        z^n \, \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top
+        \right]
+     & =
+    n \, g_{n} \, \mathbf{S}^\frac{n}{2}\pmb{\Sigma} + g_{n} \, \bar{\Sigma}^\frac{n}{2} \pmb{\Sigma}
 \end{align}
@@
 \begin{align}
-    \pmb{\Lambda}_n
+    g_n
      & \equiv
-    g_n \, \bar{\Sigma}^\frac{n}{2} \, (\pmb{\Sigma} + \mu^2\mathbf{J}_K)
-    \, +
-    K g_{n+1} \mu  \,
-    \left(
-    \mathbf{S}^\frac{n + 1}{2}
-    +
-    {\mathbf{S}^\top}^\frac{n + 1}{2}
-    \right)
-    \, +
-    n g_n \, \mathbf{S}^\frac{n}{2}\pmb{\Sigma}
+    \begin{cases}
+        \dfrac{n!}{2^\frac{n}{2} \left(\frac{n}{2}\right)!} & n \, \mathrm{even}
+        \\
+        0                                                   & n \, \mathrm{odd}
+        \quad,
+    \end{cases}
 \end{align}
-%
-and
 %
@@
     \frac{1}{K^2} \pmb{\Sigma} \, \mathbf{J}_K
+    \quad,
 \end{align}
 %
-where $\bar{\Sigma}$ is the average of all the elements in $\pmb{\Sigma}$ and
+and $\bar{\Sigma}$ is the average of all the elements in $\pmb{\Sigma}$.
+%
+Inserting these expressions into Equation~(\ref{eq:SigmaPQR}), we obtain
 %
 \begin{align}
-    g_n
+    \tilde{\pmb{\Sigma}}
      & =
-    \begin{cases}
-        \dfrac{n!}{2^\frac{n}{2} \left(\frac{n}{2}\right)!} & n \, \mathrm{even}
-        \\
-        0                                                   & n \, \mathrm{odd}
+    \resizebox{.85\hsize}{!}{$
+            \sum\limits_{n=0}^\infty
+            (-1)^n (n + 1)^2 g_n
+            \left(
+            \bar{\Sigma}^\frac{n+2}{2} \mathbf{J}_K
+            -
+            \frac{K}{\mu}\left( \mathbf{S}^\frac{n+2}{2} + {\mathbf{S}^\top}^\frac{n+2}{2} \right)
+            +
+            \frac{n}{(n+1)\mu^2}
+            \left(
+            \mathbf{S}^\frac{n}{2} \mathbf{\Sigma}
+            +
+            \bar{\Sigma}^\frac{n}{2} \mathbf{I}_K
+            \right)
+            \mathbf{\Sigma}
+            \right)
+        $}
     \quad.
-    \end{cases}
 \end{align}
+%
 %
@@
 \begin{align}
-    \pmb{E}\big[|z|\big] < 1
+    \mathbb{E}\big[|z|\big] < 1
 \end{align}
@@
 \begin{align}
-    \pmb{E}\big[z^2\big] &< 1
+    \mathbb{E}\big[z^2\big]    & < 1
     \nonumber                        \\
-    \frac{\bar{\Sigma}}{\mu^2} &< 1
+    \frac{\bar{\Sigma}}{\mu^2} & < 1
     \quad.
@@
 \appendix
+
+\xxx{THIS ALL NEEDS TO BE REWRITTEN!}
 

### 2020-11-24 notebooks/utils.py

@@ -39,7 +39,7 @@ def uprod(*idx):
         raise NotImplementedError("Case not implemented.")
 
 
-def norm_cov(mu, Sig, N=10):
+def norm_cov(mu, Sig, N=20):
     K = Sig.shape[0]
     J = np.ones((K, K))
     barSig = np.mean(Sig)
@@ -47,28 +47,22 @@ def norm_cov(mu, Sig, N=10):
     # Powers of S
     S = (Sig @ J) / K ** 2
     Spow = [np.eye(K)]
-    for n in range((N + 1) // 2):
+    for n in range((N + 2) // 2):
         Spow.append(Spow[-1] @ S)
 
-    # Zeroth order
-    norm_cov = Sig / mu ** 2
-
-    # Higher order
-    for n in range(1, N + 1):
-
-        if n % 2 == 0:
-
-            # Even correction
-            Lambda_n = (
-                g(n) * barSig ** (n // 2) * (Sig + mu ** 2 * J)
-                + n * g(n) * Spow[n // 2] @ Sig
+    # Series solution
+    norm_cov = np.zeros_like(Sig)
+    for n in range(0, N + 1, 2):
+        norm_cov += (
+            (-1) ** n
+            * (n + 1) ** 2
+            * g(n)
+            * (
+                barSig ** ((n + 2) // 2) * J
+                - K / mu * (Spow[(n + 2) // 2] + Spow[(n + 2) // 2].T)
+                + n / ((n + 1) * mu ** 2) * Spow[n // 2] @ Sig
+                + barSig ** (n // 2) / ((n + 1) * mu ** 2) * Sig
             )
-
-        else:
-
-            # Odd correction
-            Lambda_n = (K * g(n + 1) * mu) * (Spow[(n + 1) // 2] + Spow[(n + 1) // 2].T)
-
-        norm_cov += (-1) ** n * (n + 1) / mu ** (2 + n) * Lambda_n
+        )
 
     return norm_cov

### 2020-11-24 notebooks/utils.py
bugfix

@@ -50,19 +50,18 @@ def norm_cov(mu, Sig, N=20):
     for n in range((N + 2) // 2):
         Spow.append(Spow[-1] @ S)
 
-    # Series solution
     norm_cov = np.zeros_like(Sig)
     for n in range(0, N + 1, 2):
-        norm_cov += (
-            (-1) ** n
-            * (n + 1) ** 2
-            * g(n)
-            * (
-                barSig ** ((n + 2) // 2) * J
-                - K / mu * (Spow[(n + 2) // 2] + Spow[(n + 2) // 2].T)
-                + n / ((n + 1) * mu ** 2) * Spow[n // 2] @ Sig
-                + barSig ** (n // 2) / ((n + 1) * mu ** 2) * Sig
-            )
-        )
+
+        EP = (n + 1) * g(n) * barSig ** ((n + 2) // 2) * J
+        P = (-1) ** n * (n + 1) * EP
+
+        EQ = (n + 1) * K * g(n) * Spow[(n + 2) // 2]
+        Q = (-1) ** n * (n + 1) * EQ
+
+        ER = n * g(n) * Spow[n // 2] @ Sig + g(n) * barSig ** (n // 2) * Sig
+        R = (-1) ** n * (n + 1) * ER
+
+        norm_cov += (P - (Q + Q.T) + R) / (mu ** (n + 2))
 
     return norm_cov

### 2020-11-24 tex/ms.tex
bugfixes
for real now
super sketchy

@@
 \begin{align}
+    \label{eq:SigmaTildeExp}
     \tilde{\pmb{\Sigma}}
@@
      & =
-    (n + 1) g_{n} \, \bar{\Sigma}^\frac{n+2}{2} \, \mathbf{J}_K
+    \frac{(n + 1) g_{n}}{\mu^{n+2}} \, \bar{\Sigma}^\frac{n+2}{2} \, \mathbf{J}_K
     \\[0.5em]
@@
      & =
-    (n + 1) K \, g_{n} \, \mathbf{S}^\frac{n+2}{2}
+    \frac{(n + 1) K \, g_{n}}{\mu^{n+1}} \, \mathbf{S}^\frac{n+2}{2}
     \\[0.5em]
@@
      & =
-    n \, g_{n} \, \mathbf{S}^\frac{n}{2}\pmb{\Sigma} + g_{n} \, \bar{\Sigma}^\frac{n}{2} \pmb{\Sigma}
+    \frac{g_n}{\mu^n} \left(
+    n \, \mathbf{S}^\frac{n}{2}\pmb{\Sigma} + \bar{\Sigma}^\frac{n}{2} \pmb{\Sigma}
+    \right)
 \end{align}
@@
     \resizebox{.85\hsize}{!}{$
+            \frac{1}{\mu^2}
             \sum\limits_{n=0}^\infty
-            (-1)^n (n + 1)^2 g_n
+            \frac{(-1)^n (n + 1)^2 g_n}{\mu^n}
             \left(
@@
             -
-            \frac{K}{\mu}\left( \mathbf{S}^\frac{n+2}{2} + {\mathbf{S}^\top}^\frac{n+2}{2} \right)
+            K \left( \mathbf{S}^\frac{n+2}{2} + {\mathbf{S}^\top}^\frac{n+2}{2} \right)
             +
-            \frac{n}{(n+1)\mu^2}
+            \frac{1}{(n+1)}
             \left(
-            \mathbf{S}^\frac{n}{2} \mathbf{\Sigma}
+            n \mathbf{S}^\frac{n}{2}
             +
@@
     \mathbb{E}\big[z^2\big] & < 1
-    \nonumber                        \\
-    \frac{\bar{\Sigma}}{\mu^2} & < 1
     \quad.
@@
 %
+However, the quantity $z^2$ is a random variable, equal to the square of
+the weighted sum of $K$ standard normal random variables. The series therefore
+converges only if $z^2 < 1$ for \emph{all possible values} of $z^2$, a condition
+that is never strictly met except in the trivial case $\pmb{\Sigma} = \mathbf{0}$.
+This may be understood intuitively: given a (very) large number of draws from
+a Gaussian process, one of the draws will eventually correspond to a value of
+$\mathbf{x}$ whose
+mean $\bar{x}$ is arbitrarily close to zero, for which the denominators in the
+expectations in Equation~(\ref{eq:SigmaTildeExp}) diverge.
+
+While this is true for any
+$\mu$ and $\pmb{\Sigma} \ne \mathbf{0}$, in practice the probability of
+drawing $\bar{x} \approx 0$ is vanishingly small provided the expectation of
+$z^2$ is small, a condition that may be expressed as
+%
+\begin{align}
+    \frac{\bar{\Sigma}}{\mu^2} \ll 1
+    \quad.
+\end{align}
+%
+In this limit, any attempt to approximate $\tilde{\pmb{\Sigma}}$
+numerically will yield a consistent, finite solution that
+asymptotically approaches the expression derived above.
 

### 2020-11-25 notebooks/utils.py
slightly faster

@@ -44,24 +44,20 @@ def norm_cov(mu, Sig, N=20):
     J = np.ones((K, K))
     barSig = np.mean(Sig)
 
-    # Powers of S
-    S = (Sig @ J) / K ** 2
-    Spow = [np.eye(K)]
+    # Powers of S / barSig
+    G = (Sig @ J) / K ** 2 / barSig
+    Gpow = [np.eye(K)]
     for n in range((N + 2) // 2):
-        Spow.append(Spow[-1] @ S)
+        Gpow.append(Gpow[-1] @ G)
 
     norm_cov = np.zeros_like(Sig)
     for n in range(0, N + 1, 2):
+        fac = (-1) ** n * (n + 1) * g(n) * barSig ** (n // 2) / (mu ** n)
+        norm_cov += fac * (
+            Sig
+            + n * (Gpow[n // 2]) @ Sig
+            + (n + 1) * barSig * J
+            - (n + 1) * barSig * K * (Gpow[(n + 2) // 2] + Gpow[(n + 2) // 2].T)
+        )
 
-        EP = (n + 1) * g(n) * barSig ** ((n + 2) // 2) * J
-        P = (-1) ** n * (n + 1) * EP
-
-        EQ = (n + 1) * K * g(n) * Spow[(n + 2) // 2]
-        Q = (-1) ** n * (n + 1) * EQ
-
-        ER = n * g(n) * Spow[n // 2] @ Sig + g(n) * barSig ** (n // 2) * Sig
-        R = (-1) ** n * (n + 1) * ER
-
-        norm_cov += (P - (Q + Q.T) + R) / (mu ** (n + 2))
-
-    return norm_cov
+    return norm_cov / mu ** 2

### 2020-11-25 tex/ms.tex
more nbs
better:

--- 2020-11-24 tex/ms.tex
@@
 \begin{align}
-    \pmb{\mu} = \mu \, \mathbf{j}_K
+    \pmb{\mu} = \mu \, \mathbf{j}
 \end{align}
 %
-where $\mathbf{j}_K$ is the vector of $K$ ones.
+where $\mathbf{j}$ is the vector of $K$ ones.
 %
@@
     \nonumber                                                    \\[0.5em]
-     & = \frac{\mathbf{x}}{\frac{1}{K}\sum\limits_{k=0}^{K-1} x_k}
+     & = \frac{\mathbf{x}}{\frac{1}{K}\sum\limits_{k=0}^{K-1} x}
     \quad.
@@
 \begin{align}
-    \tilde{\pmb{\mu}} = \mathbf{j}_K
+    \tilde{\pmb{\mu}} = \mathbf{j}
     \quad.
@@
     \mathbb{E}\left[
-        \left(\frac{\mathbf{x}}{\bar{x}} - \mathbf{j}_K\right)
-        \left(\frac{\mathbf{x}}{\bar{x}} - \mathbf{j}_K\right)^\top
+        \left(\frac{\mathbf{x}}{\bar{x}} - \mathbf{j}\right)
+        \left(\frac{\mathbf{x}}{\bar{x}} - \mathbf{j}\right)^\top
         \right]
@@
         -
-        \frac{\mathbf{x}\,\mathbf{j}_K^\top}{\bar{x}}
+        \frac{\mathbf{x}\,\mathbf{j}^\top}{\bar{x}}
         -
-        \frac{\mathbf{j}\,\mathbf{x}_K^\top}{\bar{x}}
+        \frac{\mathbf{j}\,\mathbf{x}^\top}{\bar{x}}
         +
-        \mathbf{J}_K
+        \mathbf{j} \, \mathbf{j}^\top
         \right]
@@
     \mathbb{E}\left[
-        \frac{\mathbf{x}\,\mathbf{j}_K^\top}{\bar{x}}
+        \frac{\mathbf{x}\,\mathbf{j}^\top}{\bar{x}}
         \right]
@@
     \mathbb{E}\left[
-        \frac{\mathbf{j}_K\,\mathbf{x}^\top}{\bar{x}}
+        \frac{\mathbf{j}\,\mathbf{x}^\top}{\bar{x}}
         \right]
     +
-    \mathbf{J}_K
-    \quad,
+    \mathbf{j} \, \mathbf{j}^\top
+    \quad.
 \end{align}
 %
-where $\mathbf{J}_K = \mathbf{j}_K \mathbf{j}_K^\top$ is the $K\times K$ matrix of ones.
 To evaluate this, it is convenient to write
@@
 \begin{align}
-    \mathbf{u} \sim \mathcal{N}\left( 0, \mathbf{I}_K \right)
+    \mathbf{u} \sim \mathcal{N}\left( 0, \mathbf{I} \right)
     \quad,
@@
 %
-where $\mathbf{I}_K$ is the
+where $\mathbf{I}$ is the
 $K \times K$ identity matrix.
@@
         \frac{
-            (\pmb{\mu} + \mathbf{L} \mathbf{u})\mathbf{j}_K^\top
+            (\pmb{\mu} + \mathbf{L} \mathbf{u})\mathbf{j}^\top
         }{
@@
         \frac{
-            \mathbf{j}_K(\pmb{\mu} + \mathbf{L} \mathbf{u})^\top
+            \mathbf{j}(\pmb{\mu} + \mathbf{L} \mathbf{u})^\top
         }{
@@
     +
-    \mathbf{J}_K
+    \mathbf{j} \, \mathbf{j}^\top
 \end{align}
@@
             & =
-    \mu + \frac{1}{K}\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}
+    \mu + \frac{1}{K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}
     \nonumber                                               \\
@@
 \begin{align}
-    z \equiv \frac{1}{\mu K}\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}
+    z \equiv \frac{1}{\mu K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}
     \quad.
@@
     \mathbb{E}\Big[
-        \frac{z^2 \, \mathbf{J}_K}{(1 + z)^2}
+        \frac{z^2 \, \mathbf{j} \, \mathbf{j}^\top}{(1 + z)^2}
         \Big]
@@
     \mathbb{E}\left[
-        \frac{z\, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top}{(1 + z)^2}
+        \frac{z\, \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top}{(1 + z)^2}
         \right]
@@
 The denominator in the expressions above makes direct evaluation of the expectations
-intractable. As long as
-$\big|z| < 1$, we can Taylor expand the matrices as
+intractable. Provided
+$\big|z| < 1$ (an assumption we'll revisit below), we can Taylor expand the matrices as
 %
@@
         \,
-        \mathbf{J}_K
+        \mathbf{j} \, \mathbf{j}^\top
         \right]
@@
         \,
-        \mathbf{j}_K^\top
+        \mathbf{j}^\top
         \right]
@@
 %
-In the Appendix, we show that these may be computed from
+In the Appendix, we show that the expecations in the expressions above may be computed from
 %
@@
     \mathbb{E}\left[
-        z^{n + 2} \, \mathbf{J}_K
+        z^{n + 2} \, \mathbf{j} \, \mathbf{j}^\top
         \right]
      & =
-    (n + 1) g_{n} \, \bar{\Sigma}^\frac{n+2}{2} \, \mathbf{J}_K
+    \frac{(n + 1) g_{n} \bar{\sigma}^\frac{n+2}{2}}{\mu^{n+2}} \, \mathbf{j} \, \mathbf{j}^\top
     \\[0.5em]
     \mathbb{E}\left[
-        z^{n + 1} \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top
+        z^{n + 1} \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top
         \right]
      & =
-    (n + 1) K \, g_{n} \, \mathbf{S}^\frac{n+2}{2}
+    \frac{(n + 1) K \, g_{n} \bar{\sigma}^\frac{n}{2}}{\mu^{n+1}} \, \bar{\pmb{\sigma}} \, \mathbf{j}^\top
     \\[0.5em]
@@
      & =
-    n \, g_{n} \, \mathbf{S}^\frac{n}{2}\pmb{\Sigma} + g_{n} \, \bar{\Sigma}^\frac{n}{2} \pmb{\Sigma}
+    \frac{g_n}{\mu^n} \left(
+    n \,  \bar{\sigma}^\frac{n - 2}{2} \bar{\pmb{\sigma}} \, \bar{\pmb{\sigma}}^\top + \bar{\sigma}^\frac{n}{2} \pmb{\Sigma}
+    \right)
 \end{align}
 %
-where we define
+where
 %
@@
 %
+is the expression for the $n^\mathrm{th}$ moment of the standard normal distribution,
+%
 \begin{align}
-    \mathbf{S}
+    \bar{\pmb{\sigma}}
      & \equiv
-    \frac{1}{K^2} \pmb{\Sigma} \, \mathbf{J}_K
-    \quad,
+    \frac{1}{K} \pmb{\Sigma} \, \mathbf{j}
 \end{align}
 %
-and $\bar{\Sigma}$ is the average of all the elements in $\pmb{\Sigma}$.
+is the average of each row in $\pmb{\Sigma}$, and
 %
-Inserting these expressions into Equation~(\ref{eq:SigmaPQR}), we obtain
+\begin{align}
+    \bar{\sigma}
+     & \equiv
+    \frac{1}{K^2} \mathbf{j}^\top \pmb{\Sigma} \, \mathbf{j}
+\end{align}
+%
+is the average of all the elements in $\pmb{\Sigma}$.
+%
+Inserting these expressions into Equation~(\ref{eq:SigmaPQR}) and rearranging, we obtain
 %
@@
      & =
-    \resizebox{.85\hsize}{!}{$
-            \sum\limits_{n=0}^\infty
-            (-1)^n (n + 1)^2 g_n
+    \frac{\alpha \, \pmb{\Sigma}}{\mu^2}  +
+    \frac{\alpha \, \left(\mathbf{s} \, \mathbf{s}^\top - \bar{\pmb{\sigma}} \, \bar{\pmb{\sigma}}^\top\right)}{\mu^2 \bar{\sigma}}  +
+    \frac{\beta \, \left(\mathbf{s} \, \mathbf{s}^\top\right)}{\mu^2 \bar{\sigma}}
+\end{align}
+%
+where
+%
+\begin{align}
+    \mathbf{s}
+     & \equiv
+    \bar{\sigma} \, \mathbf{j} - \bar{\pmb{\sigma}}
+\end{align}
+%
+and
+%
+\begin{align}
+    \alpha
+     & \equiv
+    \sum\limits_{n=0}^N
+    \frac{(2n + 1)!}{2^n \, n!}
     \left(
-            \bar{\Sigma}^\frac{n+2}{2} \mathbf{J}_K
-            -
-            \frac{K}{\mu}\left( \mathbf{S}^\frac{n+2}{2} + {\mathbf{S}^\top}^\frac{n+2}{2} \right)
-            +
-            \frac{n}{(n+1)\mu^2}
+    \frac{\bar{\sigma}}{\mu^2}
+    \right)^n
+    \\[1em]
+    \beta
+     & \equiv
+    \sum\limits_{n=0}^N
+    \frac{2n(2n + 1)!}{2^n \, n!}
     \left(
-            \mathbf{S}^\frac{n}{2} \mathbf{\Sigma}
-            +
-            \bar{\Sigma}^\frac{n}{2} \mathbf{I}_K
-            \right)
-            \mathbf{\Sigma}
-            \right)
-        $}
+    \frac{\bar{\sigma}}{\mu^2}
+    \right)^n
+\end{align}
+%
+
+\xxx{...}
+
+This series is divergent!
+This may be understood intuitively: given a (very) large number of draws from
+a Gaussian process, one of the draws will eventually correspond to a value of
+$\mathbf{x}$ whose
+mean $\bar{x}$ is arbitrarily close to zero, for which the denominators in the
+expectations in Equation~(\ref{eq:SigmaTildeExp}) diverge.
+
+While this is true for any
+$\mu$ and $\pmb{\Sigma} \ne \mathbf{0}$, in practice the probability of
+drawing $\bar{x} \approx 0$ is vanishingly small provided that
+%
+\begin{align}
+    \frac{\bar{\sigma}}{\mu^2} \ll 1
     \quad.
@@
 %
-%
-The convergence criterion for this series may be written
-%
-\begin{align}
-    \mathbb{E}\big[|z|\big] < 1
-\end{align}
-%
-or, equivalently,
-%
-\begin{align}
-    \mathbb{E}\big[z^2\big]    & < 1
-    \nonumber                        \\
-    \frac{\bar{\Sigma}}{\mu^2} & < 1
-    \quad.
-\end{align}
-%
+In this limit, any attempt to approximate $\tilde{\pmb{\Sigma}}$
+numerically will yield a consistent, finite solution that
+asymptotically approaches the expression derived above.
+
+\ifdefined \includeAppendix
 
@@
     \appendix
-
-\xxx{THIS ALL NEEDS TO BE REWRITTEN!}
 
@@
             \Bigg(
-        \mu^2 \mathbf{J}_K
+            \mu^2 \mathbf{j} \, \mathbf{j}^\top
             +
-        \mu \, \mathbf{j}_K\mathbf{u}^\top \mathbf{L}^\top
+            \mu \, \mathbf{j}\mathbf{u}^\top \mathbf{L}^\top
             +
-        \mu \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top
+            \mu \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top
             +
@@
             \right]
-    - \mathbf{J}_K
+        - \mathbf{j} \, \mathbf{j}^\top
         \nonumber \\[0.5em]
@@
         \right)
-    - \mathbf{J}_K
+        - \mathbf{j} \, \mathbf{j}^\top
         \quad,
@@
     \begin{align}
-    \mathbf{P}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{J}_K \right]
+        \mathbf{P}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{j} \, \mathbf{j}^\top \right]
         \nonumber                                                                                                                                                                                \\[0.5em]
-    \mathbf{Q}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top \right]
+        \mathbf{Q}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top \right]
         \nonumber                                                                                                                                                                                \\[0.5em]
-    \mathbf{R}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top \right]
+        \mathbf{R}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top \right]
         \quad.
@@
         \\[1em]
-    \mathbb{E}\left[u_i u_j u_k\right]             & = 0
+        \mathbb{E}\left[u_i u_j u\right]             & = 0
         \\[1em]
-    \mathbb{E}\left[u_i u_j u_k u_l\right]         & =
+        \mathbb{E}\left[u_i u_j u u_l\right]         & =
         g_4 \, \delta_{i, j} \delta_{k, l} \, \delta_{i, k}
@@
         \\[1em]
-    \mathbb{E}\left[u_i u_j u_k u_l u_m\right]     & = 0
+        \mathbb{E}\left[u_i u_j u u_l u_m\right]     & = 0
         \\[1em]
-    \mathbb{E}\left[u_i u_j u_k u_l u_m u_n\right] & =
+        \mathbb{E}\left[u_i u_j u u_l u_m u_n\right] & =
         ...
@@
     \begin{align}
-    \mathbf{P}_0 & = \mathbb{E}\left[ \mathbf{J}_K \right]
+        \mathbf{P}_0 & = \mathbb{E}\left[ \mathbf{j} \, \mathbf{j}^\top \right]
         \nonumber                                                               \\
-                 & = \mathbf{J}_K
+                     & = \mathbf{j} \, \mathbf{j}^\top
     \end{align}
     %
-since $\mathbf{J}_K$ is constant. Next,
+    since $\mathbf{j} \, \mathbf{j}^\top$ is constant. Next,
     %
     \begin{align}
-    \mathbf{P}_1 & = \frac{2}{K}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{J}_K \right]
+        \mathbf{P}_1 & = \frac{2}{K}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{j} \, \mathbf{j}^\top \right]
         \nonumber                                                                                                                                \\
-                 & = \frac{2}{K}\left(\mathbf{j}_K^\top \mathbf{L} \, \mathbb{E}\left[ \mathbf{u} \right]\right) \mathbf{J}_K
+                     & = \frac{2}{K}\left(\mathbf{j}^\top \mathbf{L} \, \mathbb{E}\left[ \mathbf{u} \right]\right) \mathbf{j} \, \mathbf{j}^\top
         \nonumber                                                                                                                                \\
@@
     \begin{align}
-    \mathbf{P}_2 & = \frac{3}{K^2}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^2 \mathbf{J}_K \right]
+        \mathbf{P}_2 & = \frac{3}{K^2}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^2 \mathbf{j} \, \mathbf{j}^\top \right]
         \nonumber                                                                                                                                                                                   \\
-                 & = \frac{3}{K^2}\mathbb{E}\left[\left(\mathbf{j}_K^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j}_K \right)  \mathbf{J}_K \right]
+                     & = \frac{3}{K^2}\mathbb{E}\left[\left(\mathbf{j}^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \right)  \mathbf{j} \, \mathbf{j}^\top \right]
         \nonumber                                                                                                                                                                                   \\
-                 & = \frac{3}{K^2}\left(\mathbf{j}_K^\top \mathbf{L} \, \mathbb{E}\left[ \mathbf{u} \mathbf{u}^\top \right] \mathbf{L}^\top \, \mathbf{j}_K \right)  \mathbf{J}_K
+                     & = \frac{3}{K^2}\left(\mathbf{j}^\top \mathbf{L} \, \mathbb{E}\left[ \mathbf{u} \mathbf{u}^\top \right] \mathbf{L}^\top \, \mathbf{j} \right)  \mathbf{j} \, \mathbf{j}^\top
         \nonumber                                                                                                                                                                                   \\
-                 & = \frac{3}{K^2}\left(\mathbf{j}_K^\top \mathbf{L} \mathbf{L}^\top \, \mathbf{j}_K \right)  \mathbf{J}_K
+                     & = \frac{3}{K^2}\left(\mathbf{j}^\top \mathbf{L} \mathbf{L}^\top \, \mathbf{j} \right)  \mathbf{j} \, \mathbf{j}^\top
         \nonumber                                                                                                                                                                                   \\
-                 & = \frac{3}{K^2}\mathrm{sum}(\mathbf{\Sigma}) \mathbf{J}_K
+                     & = \frac{3}{K^2}\mathrm{sum}(\mathbf{\Sigma}) \mathbf{j} \, \mathbf{j}^\top
         \nonumber                                                                                                                                                                                   \\
-                 & = 3 \, \bar{\Sigma} \, \mathbf{J}_K
+                     & = 3 \, \bar{\sigma} \, \mathbf{j} \, \mathbf{j}^\top
     \end{align}
     %
-where $\bar{\Sigma}$ is the average of all entries in $\pmb{\Sigma}$ and
-we made use of the fact that $\mathbb{E}\left[ \mathbf{u} \mathbf{u}^\top\right] = \mathbf{I}_K$.
+    where $\bar{\sigma}$ is the average of all entries in $\pmb{\Sigma}$ and
+    we made use of the fact that $\mathbb{E}\left[ \mathbf{u} \mathbf{u}^\top\right] = \mathbf{I}$.
     %
@@
     \begin{align}
-    \mathbf{P}_3 & = \frac{4}{K^3}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^3 \mathbf{J}_K \right]
+        \mathbf{P}_3 & = \frac{4}{K^3}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^3 \mathbf{j} \, \mathbf{j}^\top \right]
         \nonumber                                                                                                                                                                                                                               \\
-                 & = \frac{4}{K^3}\mathbb{E}\left[\left(\mathbf{j}_K^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j}_K \, \mathbf{j}_K^\top \mathbf{L} \,  \mathbf{u} \right) \mathbf{J}_K \right]
+                     & = \frac{4}{K^3}\mathbb{E}\left[\left(\mathbf{j}^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \mathbf{L} \,  \mathbf{u} \right) \mathbf{j} \, \mathbf{j}^\top \right]
         \nonumber                                                                                                                                                                                                                               \\
-                 & = \frac{4}{K^3}\left(\mathbf{j}_K^\top \mathbf{L} \,  \mathbb{E}\left[\mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{J}_K \mathbf{L} \,  \mathbf{u}\right] \right) \mathbf{J}_K
+                     & = \frac{4}{K^3}\left(\mathbf{j}^\top \mathbf{L} \,  \mathbb{E}\left[\mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \mathbf{L} \,  \mathbf{u}\right] \right) \mathbf{j} \, \mathbf{j}^\top
         \nonumber                                                                                                                                                                                                                               \\
@@
     \begin{align}
-    \mathbb{E}\left[\mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{J}_K \mathbf{L} \,  \mathbf{u}\right]_{i} = \sum\limits_{k,l}(\mathbf{L}^\top \mathbf{J}_K \mathbf{L})_{kl} u_i u_k u_l = 0
+        \mathbb{E}\left[\mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \mathbf{L} \,  \mathbf{u}\right]_{i} = \sum\limits_{k,l}(\mathbf{L}^\top \mathbf{j} \, \mathbf{j}^\top \mathbf{L})_{kl} u_i u u_l = 0
         \quad,
@@
     \begin{align}
-    \mathbf{P}_4 & = \frac{5}{K^4}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^4 \mathbf{J}_K \right]
+        \mathbf{P}_4 & = \frac{5}{K^4}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^4 \mathbf{j} \, \mathbf{j}^\top \right]
         \nonumber                                                                                                                                                                                                                                                                                 \\
-                 & = \frac{5}{K^4}\mathbb{E}\left[\left(\mathbf{j}_K^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j}_K \, \mathbf{j}_K^\top \mathbf{L} \,  \mathbf{u} \, \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j}_K \right) \mathbf{J}_K \right]
+                     & = \frac{5}{K^4}\mathbb{E}\left[\left(\mathbf{j}^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \mathbf{L} \,  \mathbf{u} \, \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \right) \mathbf{j} \, \mathbf{j}^\top \right]
         \nonumber                                                                                                                                                                                                                                                                                 \\
-                 & = \frac{5}{K^4}\left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{E} \, \mathbf{L}^\top \, \mathbf{j}_K \right) \mathbf{J}_K
+                     & = \frac{5}{K^4}\left(\mathbf{j}^\top \mathbf{L} \, \mathbf{E} \, \mathbf{L}^\top \, \mathbf{j} \right) \mathbf{j} \, \mathbf{j}^\top
         \quad,
@@
     \begin{align}
-    \mathbf{A} \equiv \mathbf{L}^\top \, \mathbf{J}_K \, \mathbf{L}
+        \mathbf{A} \equiv \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \, \mathbf{L}
         \quad.
@@
         E_{ij} & =
-    \sum\limits_{k,l}A_{kl} \mathbb{E}(u_i u_j u_k u_l)
+        \sum\limits_{k,l}A_{kl} \mathbb{E}(u_i u_j u u_l)
         \nonumber  \\
@@
                & =
-    2 A_{ij} + \sum\limits_k A_{kk}
+        2 A_{ij} + \sum\limits A_{kk}
         \quad,
@@
         \mathbf{E} & =
-    2 \, \mathbf{A} + \mathrm{tr}(\mathbf{A}) \mathbf{I}_K
+        2 \, \mathbf{A} + \mathrm{tr}(\mathbf{A}) \mathbf{I}
         \nonumber      \\
                    & =
-    2 \, \mathbf{L}^\top \, \mathbf{J}_K \, \mathbf{L} + \mathrm{sum}(\pmb{\Sigma}) \mathbf{I}_K
+        2 \, \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \, \mathbf{L} + \mathrm{sum}(\pmb{\Sigma}) \mathbf{I}
         \quad.
@@
         \bigg(
-    2 \, \big(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{L}^\top \, \mathbf{J}_K \, \mathbf{L} \, \mathbf{L}^\top \, \mathbf{j}_K \big)
+        2 \, \big(\mathbf{j}^\top \mathbf{L} \, \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \, \mathbf{L} \, \mathbf{L}^\top \, \mathbf{j} \big)
         +
-    \mathrm{sum}(\pmb{\Sigma}) \big(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{L}^\top \, \mathbf{j}_K \big)
-    \bigg) \mathbf{J}_K
+        \mathrm{sum}(\pmb{\Sigma}) \big(\mathbf{j}^\top \mathbf{L} \, \mathbf{L}^\top \, \mathbf{j} \big)
+        \bigg) \mathbf{j} \, \mathbf{j}^\top
         \nonumber        \\
                      & =
-    3 \, \bar{\Sigma}^2 \mathbf{J}_K
+        3 \, \bar{\sigma}^2 \mathbf{j} \, \mathbf{j}^\top
         \quad.
@@
         \mathbf{P}_n & =
-    \mathbf{J}_K
+        \mathbf{j} \, \mathbf{j}^\top
         \begin{cases}
@@
             \\
-        g_n (n + 1) \, \bar{\Sigma}^\frac{n}{2} & n \, \mathrm{even}
+            g_n (n + 1) \, \bar{\sigma}^\frac{n}{2} & n \, \mathrm{even}
             \quad.
@@
     \begin{align}
-    \mathbf{Q}_0 & = \mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top \right]
+        \mathbf{Q}_0 & = \mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top \right]
         \nonumber                                                                                                                                              \\
-                 & = \mathbf{L} \, \mathbb{E}\left[  \mathbf{u} \right] \, \mathbf{j}_K^\top
+                     & = \mathbf{L} \, \mathbb{E}\left[  \mathbf{u} \right] \, \mathbf{j}^\top
         \nonumber                                                                                                                                              \\
@@
         %
-    \mathbf{Q}_1 & = \frac{1}{K}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top \right]
+        \mathbf{Q}_1 & = \frac{1}{K}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top \right]
         \nonumber                                                                                                                                              \\
-                 & = \frac{1}{K}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{L} \, \mathbf{u} \right] \, \mathbf{j}_K^\top
+                     & = \frac{1}{K}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{L} \, \mathbf{u} \right] \, \mathbf{j}^\top
         \nonumber                                                                                                                                              \\
-                 & = \frac{1}{K}\mathbb{E}\left[ \mathbf{L} \, \mathbf{u} (\mathbf{u}^\top \mathbf{L}^\top \mathbf{j}_K) \right] \, \mathbf{j}_K^\top
+                     & = \frac{1}{K}\mathbb{E}\left[ \mathbf{L} \, \mathbf{u} (\mathbf{u}^\top \mathbf{L}^\top \mathbf{j}) \right] \, \mathbf{j}^\top
         \nonumber                                                                                                                                              \\
-                 & = \frac{1}{K}\mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \mathbf{u}^\top \mathbf{L}^\top  \right] \, \mathbf{J}_K
+                     & = \frac{1}{K}\mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \mathbf{u}^\top \mathbf{L}^\top  \right] \, \mathbf{j} \, \mathbf{j}^\top
         \nonumber                                                                                                                                              \\
-                 & = \frac{1}{K}\mathbf{L} \, \mathbb{E}\left[  \mathbf{u} \mathbf{u}^\top   \right]  \, \mathbf{L}^\top \mathbf{J}_K
+                     & = \frac{1}{K}\mathbf{L} \, \mathbb{E}\left[  \mathbf{u} \mathbf{u}^\top   \right]  \, \mathbf{L}^\top \mathbf{j} \, \mathbf{j}^\top
         \nonumber                                                                                                                                              \\
-                 & = \frac{1}{K}\mathbf{L} \, \mathbf{L}^\top \mathbf{J}_K
+                     & = \frac{1}{K}\mathbf{L} \, \mathbf{L}^\top \mathbf{j} \, \mathbf{j}^\top
         \nonumber                                                                                                                                              \\
-                 & = \frac{1}{K}\pmb{\Sigma} \, \mathbf{J}_K
+                     & = \frac{1}{K}\pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top
     \end{align}
     %
-where we made liberal use of the fact that $\left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)$ is a scalar. Continuing,
+    where we made liberal use of the fact that $\left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)$ is a scalar. Continuing,
     %
     \begin{align}
-    \mathbf{Q}_2 & = \frac{2}{K^2}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^2 \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top \right]
+        \mathbf{Q}_2 & = \frac{2}{K^2}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^2 \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top \right]
         \nonumber                                                                                                                                                                                    \\
-                 & =  \frac{2}{K^2}\mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \, (\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}) (\mathbf{u}^\top \mathbf{L}^\top \mathbf{j}_K) \mathbf{j}_K^\top \right]
+                     & =  \frac{2}{K^2}\mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \, (\mathbf{j}^\top \mathbf{L} \, \mathbf{u}) (\mathbf{u}^\top \mathbf{L}^\top \mathbf{j}) \mathbf{j}^\top \right]
         \nonumber                                                                                                                                                                                    \\
-                 & = \frac{2}{K^2}\mathbf{L} \, \mathbb{E}\left[ \mathbf{u} \, \mathbf{j}_K^\top \mathbf{L} \, \mathbf{u} \mathbf{u}^\top \right] \, \mathbf{L}^\top \mathbf{J}_K
+                     & = \frac{2}{K^2}\mathbf{L} \, \mathbb{E}\left[ \mathbf{u} \, \mathbf{j}^\top \mathbf{L} \, \mathbf{u} \mathbf{u}^\top \right] \, \mathbf{L}^\top \mathbf{j} \, \mathbf{j}^\top
         \nonumber                                                                                                                                                                                    \\
@@
     \begin{align}
-    \mathbf{Q}_3 & = \frac{3}{K^3}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^3 \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top \right]
+        \mathbf{Q}_3 & = \frac{3}{K^3}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^3 \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top \right]
         \nonumber                                                                                                                                                  \\
@@
                      & =
-    \frac{3}{K^3}\mathbf{e} \, \mathbf{j}_K^\top
+        \frac{3}{K^3}\mathbf{e} \, \mathbf{j}^\top
     \end{align}
     %
-% 3 \, \pmb{\Sigma} \, \mathbf{J}_K \, \pmb{\Sigma} \, \mathbf{J}_K
+    % 3 \, \pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top \, \pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top
     %
@@
     \begin{align}
-    \mathbf{v} \equiv \mathbf{L}^\top \, \mathbf{j}_K
+        \mathbf{v} \equiv \mathbf{L}^\top \, \mathbf{j}
         \quad.
@@
         e_{i} & =
-    \sum\limits_{j,k,l,m}L_{ij} v_k v_l v_m \mathbb{E}(u_j u_k u_l u_m)
+        \sum\limits_{j,k,l,m}L_{ij} v v_l v_m \mathbb{E}(u_j u u_l u_m)
         \nonumber \\
               & =
-    \sum\limits_{j,k,l,m}L_{ij} v_k v_l v_m
+        \sum\limits_{j,k,l,m}L_{ij} v v_l v_m
         \Big(
@@
     \begin{align}
-    \mathbf{e} & = 3 \, \pmb{\Sigma} \, \mathbf{J}_K \, \pmb{\Sigma} \, \mathbf{j}_K
+        \mathbf{e} & = 3 \, \pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top \, \pmb{\Sigma} \, \mathbf{j}
         \quad.
@@
         \mathbf{Q}_3 & =
-    \frac{9}{K^3} \, (\pmb{\Sigma} \, \mathbf{J}_K)^2
+        \frac{9}{K^3} \, (\pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top)^2
     \end{align}
@@
             \\
-        \frac{(n + 1)g_{n+1}}{K^n} \, (\pmb{\Sigma} \, \mathbf{J}_K)^\frac{n + 1}{2} & n \, \mathrm{odd}
+            \frac{(n + 1)g_{n+1}}{K^n} \, (\pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top)^\frac{n + 1}{2} & n \, \mathrm{odd}
             \quad.
@@
         %
-    \mathbf{R}_1 & = \frac{1}{K}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top \right]
+        \mathbf{R}_1 & = \frac{1}{K}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top \right]
         \nonumber                                                                                                                                                              \\
@@
         %
-    \mathbf{R}_2 & = \mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^2 \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top \right]
+        \mathbf{R}_2 & = \mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^2 \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top \right]
         \nonumber                                                                                                                                                     \\
@@
         \nonumber                                                                                                                                                     \\
-                 & = 2 \pmb{\Sigma} \mathbf{J}_K \pmb{\Sigma} + \mathrm{sum}(\pmb{\Sigma}) \pmb{\Sigma}
+                     & = 2 \pmb{\Sigma} \mathbf{j} \, \mathbf{j}^\top \pmb{\Sigma} + \mathrm{sum}(\pmb{\Sigma}) \pmb{\Sigma}
     \end{align}
@@
         %
-    \mathbf{R}_4 & = \frac{5}{K^4}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^4 \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top \right]
+        \mathbf{R}_4 & = \frac{5}{K^4}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^4 \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top \right]
         \nonumber                                                                                                                                                                  \\
@@
         \nonumber                                                                                                                                                                  \\
-                 & = \frac{5}{K^4} \Big( 12 (\pmb{\Sigma} \mathbf{J}_K)^2 \pmb{\Sigma} + 3 \, \mathrm{sum}(\pmb{\Sigma})^2 \pmb{\Sigma} \Big)
+                     & = \frac{5}{K^4} \Big( 12 (\pmb{\Sigma} \mathbf{j} \, \mathbf{j}^\top)^2 \pmb{\Sigma} + 3 \, \mathrm{sum}(\pmb{\Sigma})^2 \pmb{\Sigma} \Big)
     \end{align}
@@
             \\
-        \frac{n (n + 1) g_{n}}{K^n} \, (\pmb{\Sigma} \, \mathbf{J}_K)^\frac{n}{2}\pmb{\Sigma} + (n + 1) g_{n} \, \bar{\Sigma}^\frac{n}{2} \pmb{\Sigma} & n \, \mathrm{even}
+            \frac{n (n + 1) g_{n}}{K^n} \, (\pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top)^\frac{n}{2}\pmb{\Sigma} + (n + 1) g_{n} \, \bar{\sigma}^\frac{n}{2} \pmb{\Sigma} & n \, \mathrm{even}
             \quad.
@@
         \bigg[
-        g_n \, \bar{\Sigma}^\frac{n}{2} \, (\pmb{\Sigma} + \mu^2\mathbf{J}_K)
+            g_n \, \bar{\sigma}^\frac{n}{2} \, (\pmb{\Sigma} + \mu^2\mathbf{j} \, \mathbf{j}^\top)
             \, +
@@
         \left(
-    \left(\pmb{\Sigma} \, \frac{\mathbf{J}_K}{K^2}\right)^\frac{n + 1}{2}
+        \left(\pmb{\Sigma} \, \frac{\mathbf{j} \, \mathbf{j}^\top}{K^2}\right)^\frac{n + 1}{2}
         +
-    \left(\frac{\mathbf{J}_K}{K^2} \, \pmb{\Sigma}\right)^\frac{n + 1}{2}
+        \left(\frac{\mathbf{j} \, \mathbf{j}^\top}{K^2} \, \pmb{\Sigma}\right)^\frac{n + 1}{2}
         \right)
@@
          & \phantom{XXXXXXXXXXXXXXX.}
-    n g_n \, \left(\pmb{\Sigma} \, \frac{\mathbf{J}_K}{K^2}\right)^\frac{n}{2}\pmb{\Sigma}
+        n g_n \, \left(\pmb{\Sigma} \, \frac{\mathbf{j} \, \mathbf{j}^\top}{K^2}\right)^\frac{n}{2}\pmb{\Sigma}
         \bigg]
@@
 
+\else
+
+    \clearpage
+
+    \appendix
+
+    See \citet{Winkelbauer2012}...
+
+\fi
+
 \bibliography{bib}
+
 \end{document}

### 2020-11-25 notebooks/utils.py

@@ -39,25 +39,28 @@ def uprod(*idx):
         raise NotImplementedError("Case not implemented.")
 
 
-def norm_cov(mu, Sig, N=20):
+def norm_cov(mu, Sig, N=10):
+
+    # Terms
     K = Sig.shape[0]
-    J = np.ones((K, K))
-    barSig = np.mean(Sig)
+    j = np.ones((K, 1))
+    sigs = np.mean(Sig)
+    sigv = (Sig @ j) / K
+    x = sigs / mu ** 2
+    s = sigs * j - sigv
 
-    # Powers of S / barSig
-    G = (Sig @ J) / K ** 2 / barSig
-    Gpow = [np.eye(K)]
-    for n in range((N + 2) // 2):
-        Gpow.append(Gpow[-1] @ G)
+    # Coefficients
+    fac = 1.0
+    alpha = 0.0
+    beta = 0.0
+    for n in range(0, N + 1):
+        alpha += fac
+        beta += 2 * n * fac
+        fac *= x * (2 * n + 3)
 
-    norm_cov = np.zeros_like(Sig)
-    for n in range(0, N + 1, 2):
-        fac = (-1) ** n * (n + 1) * g(n) * barSig ** (n // 2) / (mu ** n)
-        norm_cov += fac * (
-            Sig
-            + n * (Gpow[n // 2]) @ Sig
-            + (n + 1) * barSig * J
-            - (n + 1) * barSig * K * (Gpow[(n + 2) // 2] + Gpow[(n + 2) // 2].T)
-        )
-
-    return norm_cov / mu ** 2
+    # We're done
+    return (
+        (alpha / mu ** 2) * Sig
+        + (alpha / (mu ** 2 * sigs)) * (s @ s.T - sigv @ sigv.T)
+        + (beta / (mu ** 2 * sigs)) * (s @ s.T)
+    )

### 2020-11-27 tex/ms.tex
more text

@@
 \author{Rodrigo Luger}
+
+\section{Introduction}
+
+It is standard practice in astronomy to mean- or median- normalize datasets,
+since one is often more interested in deviations from
+some baseline than in the value of the baseline itself. This is the case,
+for example, in searches for transiting exoplanets or photometric studies
+of stellar variability, where the raw data
+consists of a timeseries of fluxes measured in counts on the detector.
+The absolute number of counts from a particular target is physically
+uninteresting, as it depends on a host of variables such as the distance to
+the target, the collecting area of the instrument, and the quantum efficiency of the
+detector. However, fractional deviations from the mean number of counts
+\emph{are} physically meaningful, as they can encode information such as the
+size of the transiting planet or the size and contrast of star spots.
+Normalization by the mean (or median) allows one to analyze data in units of (say)
+parts per million rather than counts per second.
+
+Another common practice in astronomy is to model one's data (or at least
+a component of one's data) as a Gaussian process \citep[GP; e.g.,][]{RasmussenWilliams2005}.
+GPs offer a convenient, flexible, and efficient way of modeling correlated
+data and have seen extensive use in both transiting exoplanet and stellar
+variability studies \xxx{(?)}. In one dimension, a GP is fully described
+by a mean vector $\pmb{\mu}$ and a covariance matrix $\pmb{\Sigma}$, the
+latter of which encodes information about correlations and periodicities
+in the data that are in some cases related to physical
+parameters of interest (such as the rotation period of a star or the
+lifetime of star spots).
+
+In this note, we show that these two common practices are somewhat at odds
+with each other. Specifically, if a physical process that generates
+a dataset is distributed as a GP, the normalized process \emph{cannot} be
+distributed as a GP. Provided certain conditions are met, the normalized
+process can be well \emph{approximated} by a GP, albeit one with a different
+covariance matrix $\tilde{\pmb{\Sigma}}$ that is not simply a scalar
+multiple of the original covariance matrix. Moreover, if the original process
+is described by a stationary kernel (i.e., one in which covariances are
+independent of phase), the normalized process is not guaranteed to be.
+
+For many applications, the results of this note are not likely to make
+much of a difference, since GPs are often used to model nuisance
+signals; in this case, the optimal hyperparameters describing the GP
+covariance are physically uninteresting. However, in cases where one
+wishes to interpret the GP hyperparameters in a physical context
+(such as using a periodic GP kernel to infer stellar rotation rates),
+normalizing one's data to the mean or median value can impart
+(potentially significant) bias.
 
@@
 The random variable $\tilde{\mathbf{x}}$ is no longer normally distributed, but as long as
-the variance of $\bar{x}$ is small, we can approximate it as such. Let the mean
+the variance of $\bar{x}$ is small, we can attempt to approximate it as such. Let the mean
 and covariance of $\tilde{\mathbf{x}}$ be $\tilde{\pmb{\mu}}$ and $\tilde{\pmb{\Sigma}}$, respectively:
@@
     \nonumber                                               \\
-            & = \mu(1 + z)
+            & = \mu(1 + \epsilon)
     \quad,
@@
 \begin{align}
-    z \equiv \frac{1}{\mu K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}
+    \label{eq:epsilon}
+    \epsilon
+     & \equiv \frac{\bar{x}}{\mu} - 1
+    \nonumber                                                    \\[0.5em]
+     & = \frac{1}{\mu K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}
     \quad.
@@
     \mathbb{E}\Big[
-        \frac{z^2 \, \mathbf{j} \, \mathbf{j}^\top}{(1 + z)^2}
+        \frac{\epsilon^2 \, \mathbf{j} \, \mathbf{j}^\top}{(1 + \epsilon)^2}
         \Big]
@@
     \mathbb{E}\left[
-        \frac{z\, \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top}{(1 + z)^2}
+        \frac{\epsilon\, \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top}{(1 + \epsilon)^2}
         \right]
@@
     \mathbb{E}\left[
-        \frac{ \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top}{(1 + z)^2}
+        \frac{ \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top}{(1 + \epsilon)^2}
         \right]
@@
 intractable. Provided
-$\big|z| < 1$ (an assumption we'll revisit below), we can Taylor expand the matrices as
+$\big|\epsilon| < 1$ (an assumption we'll revisit below), we can Taylor expand the matrices as
 %
 \begin{align}
+    \label{eq:WhereItAllGoesWrong1}
     \mathbf{P}
@@
     \mathbb{E}\left[
-        z^{n + 2}
+        \epsilon^{n + 2}
         \,
@@
     \\[0.5em]
+    \label{eq:WhereItAllGoesWrong2}
     \mathbf{Q}
@@
     \mathbb{E}\left[
-        z^{n + 1} \,
+        \epsilon^{n + 1} \,
         \mathbf{L}
@@
     \\[0.5em]
+    \label{eq:WhereItAllGoesWrong3}
     \mathbf{R}
@@
     \mathbb{E}\left[
-        z^n \, \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top
+        \epsilon^n \, \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top
         \right]
@@
     \mathbb{E}\left[
-        z^{n + 2} \, \mathbf{j} \, \mathbf{j}^\top
+        \epsilon^{n + 2} \, \mathbf{j} \, \mathbf{j}^\top
         \right]
@@
     \mathbb{E}\left[
-        z^{n + 1} \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top
+        \epsilon^{n + 1} \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top
         \right]
@@
 Inserting these expressions into Equation~(\ref{eq:SigmaPQR}) and rearranging, we obtain
+the final expression for the normalized covariance,
 %
 \begin{align}
+    \label{eq:SigmaTilde}
     \tilde{\pmb{\Sigma}}
@@
     \frac{\beta \, \left(\mathbf{s} \, \mathbf{s}^\top\right)}{\mu^2 \bar{\sigma}}
+    \quad,
 \end{align}
 %
-where
+where we define
 %
@@
     \bar{\sigma} \, \mathbf{j} - \bar{\pmb{\sigma}}
+    \\[1em]
+    \label{eq:alpha}
+    \alpha
+     & \equiv
+    \sum\limits_{n=0}^\infty
+    \frac{(2n + 1)!}{2^n \, n!}
+    z^n
+    \\[1em]
+    \label{eq:beta}
+    \beta
+     & \equiv
+    \sum\limits_{n=0}^\infty
+    \frac{2n(2n + 1)!}{2^n \, n!}
+    z^n
 \end{align}
 %
-and
+as well as the dimensionless parameter
 %
 \begin{align}
-    \alpha
-     & \equiv
-    \sum\limits_{n=0}^N
-    \frac{(2n + 1)!}{2^n \, n!}
-    \left(
-    \frac{\bar{\sigma}}{\mu^2}
-    \right)^n
-    \\[1em]
-    \beta
-     & \equiv
-    \sum\limits_{n=0}^N
-    \frac{2n(2n + 1)!}{2^n \, n!}
-    \left(
-    \frac{\bar{\sigma}}{\mu^2}
-    \right)^n
-\end{align}
-%
-
-\xxx{...}
-
-This series is divergent!
-This may be understood intuitively: given a (very) large number of draws from
-a Gaussian process, one of the draws will eventually correspond to a value of
-$\mathbf{x}$ whose
-mean $\bar{x}$ is arbitrarily close to zero, for which the denominators in the
-expectations in Equation~(\ref{eq:SigmaTildeExp}) diverge.
-
-While this is true for any
-$\mu$ and $\pmb{\Sigma} \ne \mathbf{0}$, in practice the probability of
-drawing $\bar{x} \approx 0$ is vanishingly small provided that
-%
-\begin{align}
-    \frac{\bar{\sigma}}{\mu^2} \ll 1
+    z & \equiv \frac{\bar{\sigma}}{\mu^2}
     \quad.
 \end{align}
+
+\section{The Bad News}
 %
-In this limit, any attempt to approximate $\tilde{\pmb{\Sigma}}$
-numerically will yield a consistent, finite solution that
-asymptotically approaches the expression derived above.
+In the previous section we derived a compact expression for
+the covariance of a normalized Gaussian process (Equation~\ref{eq:SigmaTilde}),
+which can be computed as the sum of a term proportional to the original
+covariance $\pmb{\Sigma}$ and a low-rank correction.
+%
+Unfortunately, the expressions for the scaling constants $\alpha$ and
+$\beta$ (Equations~\ref{eq:alpha} and \ref{eq:beta}) involve series
+expansions that \emph{do not converge}.
+%
+\begin{figure}[t!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/alpha_beta.pdf}
+        \oscaption{alpha_beta}{%
+            Asymptotic series expansions for $\alpha$ and $\beta$
+            (Equations~\ref{eq:alpha} and \ref{eq:beta}).
+            The left panel shows the value of each
+            coefficient ($\alpha$: solid, $\beta$: dashed)
+            as a function of the index $n$ for three
+            different values of $z$. In all cases, the value initially decreases
+            with $n$ but eventually diverges to $+\infty$ as $n \rightarrow \infty$.
+            The vertical lines indicate the optimal truncation order $N$,
+            for which the partial sums yield the best approximation to the
+            asymptotic values of the cofficients. The right panels show the
+            partial sums evaluated at each order; the value at the optimal
+            truncation order is marked with the horizontal dashed lines.
+            \label{fig:alpha_beta}
+        }
+    \end{centering}
+\end{figure}
+%
+This is demonstrated in Figure~\ref{fig:alpha_beta}, which shows the
+terms in the summations in Equations~\ref{eq:alpha} and \ref{eq:beta} for
+different values of $z$. While the terms initially decrease in magnitude
+(left panel), asymptotically approaching a finite value for both
+$\alpha$ and $\beta$ (right panels), as the expansion order increases
+the terms eventually diverge, leading to infinite values for both
+coefficients. Even though the series take longer to diverge for smaller
+values of $z$, the divergence occurs for all $z \ne 0$: i.e., the radius
+of convergence for both series is zero.
+
+Why is this? Recall the assumption we made when expanding the expectation
+integrals in Equations~(\ref{eq:WhereItAllGoesWrong1}), (\ref{eq:WhereItAllGoesWrong2}),
+and (\ref{eq:WhereItAllGoesWrong3}): the Taylor expansion converges only for
+$\big|\epsilon| < 1$. The quantity $\epsilon$ (Equation~\ref{eq:epsilon})
+is indeed small provided the sample mean $\bar{x}$ is close to the GP
+mean $\mu$. However, $\epsilon$ is a random variable, equal to
+the weighted sum of $K$ standard normal random variables. Because a normal
+distribution has infinite support, $\epsilon$ is guaranteed to take on
+values greater than unity in the limit that an infinite number of samples
+are drawn from the process. In particular, it is guaranteed to take on values
+arbitrarily close to unity, in which case the sample mean approaches zero and
+the values in the normalized sample diverge.
+This reveals a fundamental flaw in our premise:
+it is simply not correct to normalize a sample from a Gaussian process by its
+mean value, since the resulting covariance is formally infinite.
+
+Nevertheless, if one were to draw a very large number of samples from a normal
+distribution with unit mean and small standard deviation,
+the probability of drawing a sample with mean close to or smaller than zero
+is vanishingly small (for example, for $\sigma \lesssim 0.1$, this probability
+is $\lesssim 10^{-22}$).
+Any numerical (sampling) estimate of the
+covariance matrix of the normalized Gaussian process will therefore yield
+a result that asymptotically approaches a finite, consistent value as the
+number of samples increases. If it were practical to draw
+$\sim 10^{22}$ samples, however, the estimate would eventually diverge, since
+some of the normalized samples would have divergent values.
+
+This is the exact same behavior we see in the series solution above.
+While the series formally diverges, the finite asymptotic value obtained
+by truncating the expansion early can be understood as an estimate of
+the covariance of the normalized process \emph{ignoring the divergent
+tails of the distribution}.
+
+In the following sections, we empirically show that this interpretation is
+correct, and the expression for the normalized covariance
+(Equation~\ref{eq:SigmaTilde}) is accurate provided $z \ll 1$.
 
@@
         \mathbb{E}\left[
-            z^n
+            \epsilon^n
             \Bigg(
@@
 \else
-
-    \clearpage
-
-    \appendix
-
-    See \citet{Winkelbauer2012}...
-
 \fi

### 2020-11-27 tex/figures/alpha_beta.py

@@ -1,0 +1,105 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.special import loggamma
+
+
+def alpha(z, n):
+    return factorial(2 * n + 1) / (2 ** n) / factorial(n) * z ** n
+
+
+def beta(z, n):
+    return alpha(z, n) * 2 * n
+
+
+def log10_alpha(z, n):
+    return (
+        loggamma(2 * n + 2) - loggamma(n + 1) - n * np.log(2) + n * np.log(z)
+    ) / np.log(10)
+
+
+def log10_beta(z, n):
+    return log10_alpha(z, n) + np.log10(2 * n)
+
+
+# Settings
+nmax = 150
+zs = [0.005, 0.01, 0.02]
+amax = 1.10
+bmax = 0.25
+
+# Compute
+n = np.arange(0, nmax, 1)
+la = [log10_alpha(z, n) for z in zs]
+a = [np.cumsum(10 ** la[k]) for k in range(len(zs))]
+lb = [log10_beta(z, n) for z in zs]
+b = [np.cumsum(10 ** lb[k]) for k in range(len(zs))]
+
+# Setup
+fig = plt.figure(figsize=(12, 6))
+fig.subplots_adjust(wspace=0.1)
+ax_dummy = plt.subplot2grid((2, 4), (0, 0), rowspan=2, colspan=3)
+ax_coeff = ax_dummy.twinx()
+ax_alpha = plt.subplot2grid((2, 4), (0, 3))
+ax_beta = plt.subplot2grid((2, 4), (1, 3))
+
+# Plot
+for k, z in enumerate(zs):
+    ax_coeff.plot(n, la[k], "C{}-".format(k))
+    ax_coeff.plot(n, lb[k], "C{}--".format(k))
+    ax_alpha.plot(n, np.minimum(amax + 1, a[k]), "C{}-".format(k))
+    ax_beta.plot(n, np.minimum(bmax + 1, b[k]), "C{}-".format(k))
+
+# Tweak appearance
+ax_dummy.set_xscale("log")
+ax_dummy.set_yscale("log")
+log_ymin, log_ymax = ax_coeff.get_ylim()
+ax_coeff.set_ylim(log_ymin, log_ymax)
+ax_dummy.set_ylim(10 ** log_ymin, 10 ** log_ymax)
+ax_dummy.set_xlim(1, nmax * 1.1)
[…]

### 2020-11-27 tex/ms.tex
ci

@@
 %
-The denominator in the expressions above makes direct evaluation of the expectations
+The denominators in the expressions above make direct evaluation of the expectations
 intractable. Provided
@@
      & =
-    \frac{(n + 1) g_{n} \bar{\sigma}^\frac{n+2}{2}}{\mu^{n+2}} \, \mathbf{j} \, \mathbf{j}^\top
+    \frac{(n + 1) g_{n} m^\frac{n+2}{2}}{\mu^{n+2}} \, \mathbf{j} \, \mathbf{j}^\top
     \\[0.5em]
@@
      & =
-    \frac{(n + 1) K \, g_{n} \bar{\sigma}^\frac{n}{2}}{\mu^{n+1}} \, \bar{\pmb{\sigma}} \, \mathbf{j}^\top
+    \frac{(n + 1) K \, g_{n} m^\frac{n}{2}}{\mu^{n+1}} \, \mathbf{m} \, \mathbf{j}^\top
     \\[0.5em]
@@
     \frac{g_n}{\mu^n} \left(
-    n \,  \bar{\sigma}^\frac{n - 2}{2} \bar{\pmb{\sigma}} \, \bar{\pmb{\sigma}}^\top + \bar{\sigma}^\frac{n}{2} \pmb{\Sigma}
+    n \,  m^\frac{n - 2}{2} \mathbf{m} \, \mathbf{m}^\top + m^\frac{n}{2} \pmb{\Sigma}
     \right)
@@
 \begin{align}
-    \bar{\pmb{\sigma}}
+    \mathbf{m}
      & \equiv
@@
 \begin{align}
-    \bar{\sigma}
+    m
      & \equiv
@@
 %
-is the average of all the elements in $\pmb{\Sigma}$.
+is the average of all elements in $\pmb{\Sigma}$.
 %
@@
     \frac{\alpha \, \pmb{\Sigma}}{\mu^2}  +
-    \frac{\alpha \, \left(\mathbf{s} \, \mathbf{s}^\top - \bar{\pmb{\sigma}} \, \bar{\pmb{\sigma}}^\top\right)}{\mu^2 \bar{\sigma}}  +
-    \frac{\beta \, \left(\mathbf{s} \, \mathbf{s}^\top\right)}{\mu^2 \bar{\sigma}}
+    \frac{\alpha \, \left(\mathbf{s} \, \mathbf{s}^\top - \mathbf{m} \, \mathbf{m}^\top\right)}{\mu^2 m}  +
+    \frac{\beta \, \left(\mathbf{s} \, \mathbf{s}^\top\right)}{\mu^2 m}
     \quad,
@@
      & \equiv
-    \bar{\sigma} \, \mathbf{j} - \bar{\pmb{\sigma}}
+    m \, \mathbf{j} - \mathbf{m}
     \\[1em]
@@
 \begin{align}
-    z & \equiv \frac{\bar{\sigma}}{\mu^2}
-    \quad.
+    z & \equiv \frac{m}{\mu^2}
+    \quad,
 \end{align}
+%
+equal to the average element of the covariance matrix divided by the square of the
+GP mean.
 
@@
 In the following sections, we empirically show that this interpretation is
-correct, and the expression for the normalized covariance
+correct, and that the expression for the normalized covariance
 (Equation~\ref{eq:SigmaTilde}) is accurate provided $z \ll 1$.
@@
         \nonumber                                                                                                                                                                                   \\
-                     & = 3 \, \bar{\sigma} \, \mathbf{j} \, \mathbf{j}^\top
+                     & = 3 \, m \, \mathbf{j} \, \mathbf{j}^\top
     \end{align}
     %
-    where $\bar{\sigma}$ is the average of all entries in $\pmb{\Sigma}$ and
+    where $m$ is the average of all entries in $\pmb{\Sigma}$ and
     we made use of the fact that $\mathbb{E}\left[ \mathbf{u} \mathbf{u}^\top\right] = \mathbf{I}$.
@@
                      & =
-        3 \, \bar{\sigma}^2 \mathbf{j} \, \mathbf{j}^\top
+        3 \, m^2 \mathbf{j} \, \mathbf{j}^\top
         \quad.
@@
             \\
-            g_n (n + 1) \, \bar{\sigma}^\frac{n}{2} & n \, \mathrm{even}
+            g_n (n + 1) \, m^\frac{n}{2} & n \, \mathrm{even}
             \quad.
@@
             \\
-            \frac{n (n + 1) g_{n}}{K^n} \, (\pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top)^\frac{n}{2}\pmb{\Sigma} + (n + 1) g_{n} \, \bar{\sigma}^\frac{n}{2} \pmb{\Sigma} & n \, \mathrm{even}
+            \frac{n (n + 1) g_{n}}{K^n} \, (\pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top)^\frac{n}{2}\pmb{\Sigma} + (n + 1) g_{n} \, m^\frac{n}{2} \pmb{\Sigma} & n \, \mathrm{even}
             \quad.
@@
         \bigg[
-            g_n \, \bar{\sigma}^\frac{n}{2} \, (\pmb{\Sigma} + \mu^2\mathbf{j} \, \mathbf{j}^\top)
+            g_n \, m^\frac{n}{2} \, (\pmb{\Sigma} + \mu^2\mathbf{j} \, \mathbf{j}^\top)
             \, +

### 2020-11-27 notebooks/utils.py

@@ -44,10 +44,10 @@ def norm_cov(mu, Sig, N=10):
     # Terms
     K = Sig.shape[0]
     j = np.ones((K, 1))
-    sigs = np.mean(Sig)
-    sigv = (Sig @ j) / K
-    x = sigs / mu ** 2
-    s = sigs * j - sigv
+    m = np.mean(Sig)
+    mvec = (Sig @ j) / K
+    x = m / mu ** 2
+    s = m * j - mvec
 
     # Coefficients
     fac = 1.0
@@ -61,6 +61,6 @@ def norm_cov(mu, Sig, N=10):
     # We're done
     return (
         (alpha / mu ** 2) * Sig
-        + (alpha / (mu ** 2 * sigs)) * (s @ s.T - sigv @ sigv.T)
-        + (beta / (mu ** 2 * sigs)) * (s @ s.T)
+        + (alpha / (mu ** 2 * m)) * (s @ s.T - mvec @ mvec.T)
+        + (beta / (mu ** 2 * m)) * (s @ s.T)
     )

### 2020-11-27 notebooks/utils.py
listofitems override v1.61

@@ -39,7 +39,7 @@ def uprod(*idx):
         raise NotImplementedError("Case not implemented.")
 
 
-def norm_cov(mu, Sig, N=10):
+def norm_cov(mu, Sig, N=20):
 
     # Terms
     K = Sig.shape[0]

### 2020-11-28 tex/figures/periodic.py
new fig

@@ -1,0 +1,76 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import george
+from george.kernels import CosineKernel
+
+
+def norm_cov(mu, Sig, N=20):
+
+    # Terms
+    K = Sig.shape[0]
+    j = np.ones((K, 1))
+    m = np.mean(Sig)
+    mvec = (Sig @ j) / K
+    x = m / mu ** 2
+    s = m * j - mvec
+
+    # Coefficients
+    fac = 1.0
+    alpha = 0.0
+    beta = 0.0
+    for n in range(0, N + 1):
+        alpha += fac
+        beta += 2 * n * fac
+        fac *= x * (2 * n + 3)
+
+    # We're done
+    return (
+        (alpha / mu ** 2) * Sig
+        + (alpha / (mu ** 2 * m)) * (s @ s.T - mvec @ mvec.T)
+        + (beta / (mu ** 2 * m)) * (s @ s.T)
+    )
+
+
+# GP Mean
+mu = 0.75
+
+# GP Amplitude
+std = 0.1
+
+# Asymmetry term
+offset = 0.5
+
+# Dimension
+K = 1000
+
+# Expansion order in our series solution
+N = 20
+
+# Get the covariance matrix
+t = np.linspace(0, 1, K)
+period = 0.75
+kernel = std ** 2 * (offset + CosineKernel(np.log(period)))
+gp = george.GP(kernel)
+gp.compute(t)
+Sigma = gp.get_matrix(t)
+
+# Compute the normalized covariance using the series expansion
+Sigma_norm = norm_cov(mu, Sigma, N=N)
+
+# Figure setup
+fig, ax = plt.subplots(1, 2, figsize=(12, 6))
+vmin = Sigma_norm.min()
+vmax = Sigma_norm.max()
+
+ax[0].imshow(Sigma, cmap="viridis", vmin=vmin, vmax=vmax)
+ax[1].imshow(Sigma_norm, cmap="viridis", vmin=vmin, vmax=vmax)
+
+ax[0].set_title(r"$\mathbf{\Sigma}$", fontsize=25)
+ax[1].set_title(r"$\mathbf{\tilde{\Sigma}}$", fontsize=25)
+
+for axis in ax:
+    axis.set_xticks([])
+    axis.set_yticks([])
+
+# We're done
+fig.savefig(__file__.replace(".py", ".pdf"), bbox_inches="tight")

### 2020-11-29 tex/ms.tex
new fig
more figures

@@
 
+\section{Non-stationarity}
+
+%
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/periodic.pdf}
+        \oscaption{periodic}{%
+            The covariance matrix corresponding to a periodic kernel
+            (left) and the covariance matrix of the corresponding
+            normalized process (right), plotted on the same color scale.
+            In addition to an offset and
+            an overall scaling relative to the original, the normalized
+            process is noticeably non-stationary.
+            \label{fig:periodic}
+        }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/periodic_error.pdf}
+        \oscaption{periodic_error}{%
+            The covariance of the same normalized process as in
+            Figure~\ref{fig:periodic}, but computed numerically
+            from $10^5$ samples from the GP
+            (left). The right panel shows the relative difference
+            between the series solution and the numerical solution,
+            normalized to the largest element in $\pmb{\tilde{\Sigma}}$.
+            The maximum difference between the two solutions is less
+            than one percent and is within the error of the numerical
+            estimate.
+            \label{fig:periodic_error}
+        }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/periodic_error_asymptotic.pdf}
+        \oscaption{periodic_error_asymptotic}{%
+            Maximum (blue) and median (orange) normalized relative difference
+            between the series solution and the numerical estimate of the
+            covariance of the normalized process, as a function of the
+            number of samples in the numerical estimate. Thin lines show the
+            result of individual trials; thick lines correspond to the average
+            over 30 trials.
+            \label{fig:periodic_error_asymptotic}
+        }
+    \end{centering}
+\end{figure}
+
 \ifdefined \includeAppendix
-
-    \clearpage
-
-    \appendix
-
-    \section{Computing $\tilde{\pmb{\Sigma}}$}
-    %
-    Since the expectation is a linear operator, we can write Equation~(\ref{eq:SigmaTildeExp})
-    as
-    %
-    \begin{align}
-        \tilde{\pmb{\Sigma}}
-         & =
-        \frac{1}{\mu^2}
-        \sum\limits_{n=0}^\infty
-        (-1)^n (n + 1)
-        \,
-        \mathbb{E}\left[
-            \epsilon^n
-            \Bigg(
-            \mu^2 \mathbf{j} \, \mathbf{j}^\top
-            +
-            \mu \, \mathbf{j}\mathbf{u}^\top \mathbf{L}^\top
-            +
-            \mu \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top
-            +
-            \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top
-            \Bigg)
-            \right]
-        - \mathbf{j} \, \mathbf{j}^\top
-        \nonumber \\[0.5em]
-         & =
-        \sum\limits_{n=0}^\infty
-        \frac{(-1)^n}{\mu^{2 + n}}
-        \,
-        \left(
-        \mu^2 \mathbf{P}_n
-        +
-        \mu \, \mathbf{Q}_n
-        +
-        \mu \, \mathbf{Q}_n^\top
-        +
-        \mathbf{R}_n
-        \right)
-        - \mathbf{j} \, \mathbf{j}^\top
-        \quad,
-    \end{align}
-    %
-    where we define the matrices
-    %
-    \begin{align}
-        \mathbf{P}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{j} \, \mathbf{j}^\top \right]
-        \nonumber                                                                                                                                                                                \\[0.5em]
-        \mathbf{Q}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top \right]
-        \nonumber                                                                                                                                                                                \\[0.5em]
-        \mathbf{R}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top \right]
-        \quad.
-    \end{align}
-    %
-    In order to compute these matrices,
-    we will make use of the expression for the
-    $n^\mathrm{th}$ moment of the standard normal distribution:
-    %
-    \begin{align}
-        \mathbb{E}\left[ u^n \right] & = g_n
-    \end{align}
-    %
-    for scalar $u \sim \mathcal{N}(0, 1)$, where
-    %
-    \begin{align}
-        g_n
-         & =
-        \begin{cases}
-            \dfrac{n!}{2^\frac{n}{2} \left(\frac{n}{2}\right)!} & n \, \mathrm{even}
-            \\
-            0                                                   & n \, \mathrm{odd}
-            \quad.
-        \end{cases}
-    \end{align}
-    %
-    \citep[e.g.,][]{Winkelbauer2012}.
-    We can apply this relation to compute expectations
-    of products of the components of a random standard normal vector $\mathbf{u}$:
-    %
-    \begin{align}
-        \mathbb{E}\left[u_i \right]                  & = 0
-        \\[1em]
-        \mathbb{E}\left[u_i u_j\right]               & = g_2
-        \\[1em]
-        \mathbb{E}\left[u_i u_j u\right]             & = 0
-        \\[1em]
-        \mathbb{E}\left[u_i u_j u u_l\right]         & =
-        g_4 \, \delta_{i, j} \delta_{k, l} \, \delta_{i, k}
-        +
-        g_2^2 \left(
-        \delta_{i, j} \, \delta_{k, l} \, \bar{\delta}_{i, k}
-        +
-        \delta_{i, k} \, \delta_{j, l} \, \bar{\delta}_{i, j}
-        +
-        \delta_{i, l} \, \delta_{j, k} \, \bar{\delta}_{i, j}
-        \right)
-        \\[1em]
-        \mathbb{E}\left[u_i u_j u u_l u_m\right]     & = 0
-        \\[1em]
-        \mathbb{E}\left[u_i u_j u u_l u_m u_n\right] & =
-        ...
-        \quad,
-    \end{align}
-    %
-    where $\delta$ is the Kronecker delta and $\bar{\delta} \equiv 1 - \delta$.
-
-    \subsection{The $\mathbf{P}$ expectation}
-
-    Let us begin by computing the first several terms in $\mathbf{P}$.
-    %
-    \begin{align}
-        \mathbf{P}_0 & = \mathbb{E}\left[ \mathbf{j} \, \mathbf{j}^\top \right]
-        \nonumber                                                               \\
-                     & = \mathbf{j} \, \mathbf{j}^\top
-    \end{align}
-    %
-    since $\mathbf{j} \, \mathbf{j}^\top$ is constant. Next,
-    %
-    \begin{align}
-        \mathbf{P}_1 & = \frac{2}{K}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{j} \, \mathbf{j}^\top \right]
-        \nonumber                                                                                                                                \\
-                     & = \frac{2}{K}\left(\mathbf{j}^\top \mathbf{L} \, \mathbb{E}\left[ \mathbf{u} \right]\right) \mathbf{j} \, \mathbf{j}^\top
-        \nonumber                                                                                                                                \\
-                     & = \mathbf{0}
-    \end{align}
-    %
-    since $\mathbb{E}\left[ \mathbf{u} \right] = \mathbf{0}$. The next term is
-    %
-    \begin{align}
-        \mathbf{P}_2 & = \frac{3}{K^2}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^2 \mathbf{j} \, \mathbf{j}^\top \right]
-        \nonumber                                                                                                                                                                                   \\
-                     & = \frac{3}{K^2}\mathbb{E}\left[\left(\mathbf{j}^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \right)  \mathbf{j} \, \mathbf{j}^\top \right]
-        \nonumber                                                                                                                                                                                   \\
-                     & = \frac{3}{K^2}\left(\mathbf{j}^\top \mathbf{L} \, \mathbb{E}\left[ \mathbf{u} \mathbf{u}^\top \right] \mathbf{L}^\top \, \mathbf{j} \right)  \mathbf{j} \, \mathbf{j}^\top
-        \nonumber                                                                                                                                                                                   \\
-                     & = \frac{3}{K^2}\left(\mathbf{j}^\top \mathbf{L} \mathbf{L}^\top \, \mathbf{j} \right)  \mathbf{j} \, \mathbf{j}^\top
-        \nonumber                                                                                                                                                                                   \\
-                     & = \frac{3}{K^2}\mathrm{sum}(\mathbf{\Sigma}) \mathbf{j} \, \mathbf{j}^\top
-        \nonumber                                                                                                                                                                                   \\
-                     & = 3 \, m \, \mathbf{j} \, \mathbf{j}^\top
-    \end{align}
-    %
-    where $m$ is the average of all entries in $\pmb{\Sigma}$ and
-    we made use of the fact that $\mathbb{E}\left[ \mathbf{u} \mathbf{u}^\top\right] = \mathbf{I}$.
-    %
-    Next,
-    %
-    \begin{align}
-        \mathbf{P}_3 & = \frac{4}{K^3}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^3 \mathbf{j} \, \mathbf{j}^\top \right]
-        \nonumber                                                                                                                                                                                                                               \\
-                     & = \frac{4}{K^3}\mathbb{E}\left[\left(\mathbf{j}^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \mathbf{L} \,  \mathbf{u} \right) \mathbf{j} \, \mathbf{j}^\top \right]
-        \nonumber                                                                                                                                                                                                                               \\
-                     & = \frac{4}{K^3}\left(\mathbf{j}^\top \mathbf{L} \,  \mathbb{E}\left[\mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \mathbf{L} \,  \mathbf{u}\right] \right) \mathbf{j} \, \mathbf{j}^\top
-        \nonumber                                                                                                                                                                                                                               \\
-                     & = \mathbf{0}
-    \end{align}
-    %
-    where we made use of the fact that we may write the component at index $i$ of the vector within the expectation in the next-to-last line
-    as
-    \begin{align}
-        \mathbb{E}\left[\mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \mathbf{L} \,  \mathbf{u}\right]_{i} = \sum\limits_{k,l}(\mathbf{L}^\top \mathbf{j} \, \mathbf{j}^\top \mathbf{L})_{kl} u_i u u_l = 0
-        \quad,
-        \nonumber
-    \end{align}
-    %
-    which is zero since it is the product of an odd number of random normal variables.
-    Finally,
-    %
-    \begin{align}
-        \mathbf{P}_4 & = \frac{5}{K^4}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^4 \mathbf{j} \, \mathbf{j}^\top \right]
-        \nonumber                                                                                                                                                                                                                                                                                 \\
-                     & = \frac{5}{K^4}\mathbb{E}\left[\left(\mathbf{j}^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \mathbf{L} \,  \mathbf{u} \, \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \right) \mathbf{j} \, \mathbf{j}^\top \right]
-        \nonumber                                                                                                                                                                                                                                                                                 \\
-                     & = \frac{5}{K^4}\left(\mathbf{j}^\top \mathbf{L} \, \mathbf{E} \, \mathbf{L}^\top \, \mathbf{j} \right) \mathbf{j} \, \mathbf{j}^\top
-        \quad,
-    \end{align}
-    %
-    where we define
-    %
-    \begin{align}
-        \mathbf{E} \equiv \mathbb{E}\left[ \mathbf{u} \mathbf{u}^\top  \mathbf{A} \,  \mathbf{u} \mathbf{u}^\top \right]
-    \end{align}
-    %
-    and
-    %
-    \begin{align}
-        \mathbf{A} \equiv \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \, \mathbf{L}
-        \quad.
-    \end{align}
-    %
-    The components of this matrix are
-    %
-    \begin{align}
-        E_{ij} & =
-        \sum\limits_{k,l}A_{kl} \mathbb{E}(u_i u_j u u_l)
-        \nonumber  \\
-               & =
-        \sum\limits_{k,l}A_{kl}
-        \Big(
-        g_4 \, \delta_{i, j} \, \delta_{k, l} \, \delta_{i, k}
-        +
-        g_2^2 \big(
-            \delta_{i, j} \, \delta_{k, l} \, \bar{\delta}_{i, k}
-            +
-            \delta_{i, k} \, \delta_{j, l} \, \bar{\delta}_{i, j}
-            +
-            \delta_{i, l} \, \delta_{j, k} \, \bar{\delta}_{i, j}
-            \big)
-        \Big)
-        \nonumber  \\
-               & =
-        2 A_{ij} + \sum\limits A_{kk}
-        \quad,
-    \end{align}
-    %
-    where we used the fact that $\mathbf{A} = \mathbf{A}^\top$. We may thus write
-    %
-    \begin{align}
-        \mathbf{E} & =
-        2 \, \mathbf{A} + \mathrm{tr}(\mathbf{A}) \mathbf{I}
-        \nonumber      \\
-                   & =
-        2 \, \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \, \mathbf{L} + \mathrm{sum}(\pmb{\Sigma}) \mathbf{I}
-        \quad.
-    \end{align}
-    %
-    Inserting this back into the expression for $\mathbf{P}_4$, we obtain
-    %
-    \begin{align}
-        \mathbf{P}_4 & =
-        \frac{5}{K^4}
-        \bigg(
-        2 \, \big(\mathbf{j}^\top \mathbf{L} \, \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \, \mathbf{L} \, \mathbf{L}^\top \, \mathbf{j} \big)
-        +
-        \mathrm{sum}(\pmb{\Sigma}) \big(\mathbf{j}^\top \mathbf{L} \, \mathbf{L}^\top \, \mathbf{j} \big)
-        \bigg) \mathbf{j} \, \mathbf{j}^\top
-        \nonumber        \\
-                     & =
-        3 \, m^2 \mathbf{j} \, \mathbf{j}^\top
-        \quad.
-    \end{align}
-    %
-    The general term in this sequence is
-    %
-    \begin{align}
-        \mathbf{P}_n & =
-        \mathbf{j} \, \mathbf{j}^\top
-        \begin{cases}
-            0                            & n \, \mathrm{odd}
-            \\
-            g_n (n + 1) \, m^\frac{n}{2} & n \, \mathrm{even}
-            \quad.
-        \end{cases}
-    \end{align}
-    %
-
-    \subsection{The $\mathbf{Q}$ expectation}
-    %
-    Let us again compute the first several terms of this expectation matrix.
-    %
-    \begin{align}
-        \mathbf{Q}_0 & = \mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top \right]
-        \nonumber                                                                                                                                              \\
-                     & = \mathbf{L} \, \mathbb{E}\left[  \mathbf{u} \right] \, \mathbf{j}^\top
-        \nonumber                                                                                                                                              \\
-                     & = \mathbf{0}
-        %
-        \\[1em]
-        %
-        \mathbf{Q}_1 & = \frac{1}{K}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top \right]
-        \nonumber                                                                                                                                              \\
-                     & = \frac{1}{K}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{L} \, \mathbf{u} \right] \, \mathbf{j}^\top
-        \nonumber                                                                                                                                              \\
-                     & = \frac{1}{K}\mathbb{E}\left[ \mathbf{L} \, \mathbf{u} (\mathbf{u}^\top \mathbf{L}^\top \mathbf{j}) \right] \, \mathbf{j}^\top
-        \nonumber                                                                                                                                              \\
-                     & = \frac{1}{K}\mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \mathbf{u}^\top \mathbf{L}^\top  \right] \, \mathbf{j} \, \mathbf{j}^\top
-        \nonumber                                                                                                                                              \\
-                     & = \frac{1}{K}\mathbf{L} \, \mathbb{E}\left[  \mathbf{u} \mathbf{u}^\top   \right]  \, \mathbf{L}^\top \mathbf{j} \, \mathbf{j}^\top
-        \nonumber                                                                                                                                              \\
-                     & = \frac{1}{K}\mathbf{L} \, \mathbf{L}^\top \mathbf{j} \, \mathbf{j}^\top
-        \nonumber                                                                                                                                              \\
-                     & = \frac{1}{K}\pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top
-    \end{align}
-    %
-    where we made liberal use of the fact that $\left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)$ is a scalar. Continuing,
-    %
-    \begin{align}
-        \mathbf{Q}_2 & = \frac{2}{K^2}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^2 \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top \right]
-        \nonumber                                                                                                                                                                                    \\
-                     & =  \frac{2}{K^2}\mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \, (\mathbf{j}^\top \mathbf{L} \, \mathbf{u}) (\mathbf{u}^\top \mathbf{L}^\top \mathbf{j}) \mathbf{j}^\top \right]
-        \nonumber                                                                                                                                                                                    \\
-                     & = \frac{2}{K^2}\mathbf{L} \, \mathbb{E}\left[ \mathbf{u} \, \mathbf{j}^\top \mathbf{L} \, \mathbf{u} \mathbf{u}^\top \right] \, \mathbf{L}^\top \mathbf{j} \, \mathbf{j}^\top
-        \nonumber                                                                                                                                                                                    \\
-                     & = \mathbf{0}
-    \end{align}
-    %
-    since again the components of the expectation in the next-to-last line involve products of three standard normal random variables.
-    Next,
-    \begin{align}
-        \mathbf{Q}_3 & = \frac{3}{K^3}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^3 \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top \right]
-        \nonumber                                                                                                                                                  \\
-                     & = \xxx{...}
-        \nonumber                                                                                                                                                  \\
-                     & =
-        \frac{3}{K^3}\mathbf{e} \, \mathbf{j}^\top
-    \end{align}
-    %
-    % 3 \, \pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top \, \pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top
-    %
-    where we define
-    %
-    \begin{align}
-        \mathbf{e} \equiv \mathbb{E}\left[
-            \left(
-            \mathbf{v}^\top \mathbf{u} \mathbf{u}^\top \mathbf{v}
-            \mathbf{v}^\top \mathbf{u}
-            \right)
-            \mathbf{L} \mathbf{u}
-            \right]
-    \end{align}
-    %
-    and
-    %
-    \begin{align}
-        \mathbf{v} \equiv \mathbf{L}^\top \, \mathbf{j}
-        \quad.
-    \end{align}
-    %
-    The components of $\mathbf{e}$ are given by
-    %
-    \begin{align}
-        e_{i} & =
-        \sum\limits_{j,k,l,m}L_{ij} v v_l v_m \mathbb{E}(u_j u u_l u_m)
-        \nonumber \\
-              & =
-        \sum\limits_{j,k,l,m}L_{ij} v v_l v_m
-        \Big(
-        g_4 \, \delta_{j, k} \, \delta_{l, m} \, \delta_{j, l}
-        +
-        g_2^2 \big(
-            \delta_{j, k} \, \delta_{l, m} \, \bar{\delta}_{j, l}
-            +
-            \delta_{j, l} \, \delta_{k, m} \, \bar{\delta}_{j, k}
-            +
-            \delta_{j, m} \, \delta_{k, l} \, \bar{\delta}_{j, k}
-            \big)
-        \Big)
-        \nonumber \\
-              & =
-        \xxx{...}
-    \end{align}
-    %
-    We may thus write
-    %
-    \begin{align}
-        \mathbf{e} & = 3 \, \pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top \, \pmb{\Sigma} \, \mathbf{j}
-        \quad.
-    \end{align}
-    %
-    Inserting this back into the expression for $\mathbf{Q}_3$, we obtain
-    %
-    \begin{align}
-        \mathbf{Q}_3 & =
-        \frac{9}{K^3} \, (\pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top)^2
-    \end{align}
-    %
-    Based on this pattern, the general term in $\mathbf{Q}$ is
-    %
-    \begin{align}
-        \mathbf{Q}_n & =
-        \begin{cases}
-            \mathbf{0}                                                                                    & n \, \mathrm{even}
-            \\
-            \frac{(n + 1)g_{n+1}}{K^n} \, (\pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top)^\frac{n + 1}{2} & n \, \mathrm{odd}
-            \quad.
-        \end{cases}
-    \end{align}
-
-    \subsection{The $\mathbf{R}$ expectation}
-    %
-    The first several terms in $\mathbf{R}$ are given by
-    %
-    \setlength{\abovedisplayskip}{1em}
-    \begin{align}
-        \mathbf{R}_0 & = \mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top \right]
-        \nonumber                                                                                                                                                              \\
-                     & = \mathbf{L} \, \mathbb{E}\left[  \mathbf{u} \, \mathbf{u}^\top \right] \, \mathbf{L}^\top
-        \nonumber                                                                                                                                                              \\
-                     & = \pmb{\Sigma}
-        %
-        \\[1em]
-        %
-        \mathbf{R}_1 & = \frac{1}{K}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top \right]
-        \nonumber                                                                                                                                                              \\
-                     & = \mathbf{0}
-        %
-    \end{align}
-    %
-    since its elements are all products of three standard normal random variables. Next,
-    %
-    \begin{align}
-        %
-        \mathbf{R}_2 & = \mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^2 \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top \right]
-        \nonumber                                                                                                                                                     \\
-                     & = \xxx{...}
-        \nonumber                                                                                                                                                     \\
-                     & = 2 \pmb{\Sigma} \mathbf{j} \, \mathbf{j}^\top \pmb{\Sigma} + \mathrm{sum}(\pmb{\Sigma}) \pmb{\Sigma}
-    \end{align}
-    %
-    \xxx{By trial and error, I found that}
-    %
-    \begin{align}
-        %
-        \mathbf{R}_4 & = \frac{5}{K^4}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^4 \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top \right]
-        \nonumber                                                                                                                                                                  \\
-                     & = \xxx{...}
-        \nonumber                                                                                                                                                                  \\
-                     & = \frac{5}{K^4} \Big( 12 (\pmb{\Sigma} \mathbf{j} \, \mathbf{j}^\top)^2 \pmb{\Sigma} + 3 \, \mathrm{sum}(\pmb{\Sigma})^2 \pmb{\Sigma} \Big)
-    \end{align}
-    %
-    Based on this pattern, the general term in $\mathbf{R}$ is
-    %
-    \begin{align}
-        \mathbf{R}_n & =
-        \begin{cases}
-            \mathbf{0}                                                                                                                                           & n \, \mathrm{odd}
-            \\
-            \frac{n (n + 1) g_{n}}{K^n} \, (\pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top)^\frac{n}{2}\pmb{\Sigma} + (n + 1) g_{n} \, m^\frac{n}{2} \pmb{\Sigma} & n \, \mathrm{even}
-            \quad.
-        \end{cases}
-    \end{align}
-
-    \subsection{The final result}
-    Inserting the matrices $\mathbf{P}$, $\mathbf{Q}$, and $\mathbf{R}$ into the expression
-    for $\tilde{\pmb{\Sigma}}$ and rearranging,
-    we obtain
-    %
-    \begin{align}
-        \tilde{\pmb{\Sigma}}
-         & =
-        \frac{1}{\mu^2} \pmb{\Sigma}
-        +
-        \frac{1}{\mu^2}
-        \sum\limits_{n=1}^\infty
-        \frac{(-1)^n(n + 1)}{\mu^{n}}
-        \,
-        \bigg[
-            g_n \, m^\frac{n}{2} \, (\pmb{\Sigma} + \mu^2\mathbf{j} \, \mathbf{j}^\top)
-            \, +
-            \nonumber                 \\[0.5em]
-         & \phantom{XXXXXXXXXXXXXXX.}
-        K g_{n+1} \mu  \,
-        \left(
-        \left(\pmb{\Sigma} \, \frac{\mathbf{j} \, \mathbf{j}^\top}{K^2}\right)^\frac{n + 1}{2}
-        +
-        \left(\frac{\mathbf{j} \, \mathbf{j}^\top}{K^2} \, \pmb{\Sigma}\right)^\frac{n + 1}{2}
-        \right)
-        \, +
-        \nonumber                     \\[0.5em]
-         & \phantom{XXXXXXXXXXXXXXX.}
-        n g_n \, \left(\pmb{\Sigma} \, \frac{\mathbf{j} \, \mathbf{j}^\top}{K^2}\right)^\frac{n}{2}\pmb{\Sigma}
-        \bigg]
-        \quad.
-    \end{align}
-
+    \input{appendix}
 \else

### 2020-11-29 tex/figures/periodic_error.py

@@ -3,6 +3,7 @@ import matplotlib.pyplot as plt
 from mpl_toolkits.axes_grid1 import make_axes_locatable
 import george
 from george.kernels import CosineKernel
+from scipy.linalg import cho_factor
 
 
 def norm_cov(mu, Sig, N=20):
@@ -47,39 +48,60 @@ K = 1000
 # Expansion order in our series solution
 N = 20
 
+# Number of samples in numerical estimate
+M = 100000
+
 # Get the covariance matrix
 t = np.linspace(0, 1, K)
 period = 0.75
 kernel = std ** 2 * (offset + CosineKernel(np.log(period)))
 gp = george.GP(kernel)
 gp.compute(t)
-Sigma = gp.get_matrix(t)
+Sigma = gp.get_matrix(t) + 1e-12 * np.eye(K)
 
 # Compute the normalized covariance using the series expansion
 Sigma_norm = norm_cov(mu, Sigma, N=N)
 
+# Compute it numerically by sampling
+np.random.seed(0)
+L = np.tril(cho_factor(Sigma, lower=True)[0])
+u = np.random.randn(K, M)
+x = mu + L @ u
+xnorm = x / np.mean(x, axis=0).reshape(1, -1)
+Sigma_norm_num = np.cov(xnorm)
+
 # Figure setup
 fig, ax = plt.subplots(1, 2, figsize=(12, 6))
-vmin = Sigma_norm.min()
-vmax = Sigma_norm.max()
+# fig.subplots_adjust(wspace=0.05)
+vmin = np.hstack((Sigma_norm, Sigma_norm_num)).min()
+vmax = np.hstack((Sigma_norm, Sigma_norm_num)).max()
 
-# Original
-im = ax[0].imshow(Sigma, cmap="viridis", vmin=vmin, vmax=vmax)
+# Numerical solution
+im = ax[0].imshow(Sigma_norm_num, cmap="viridis", vmin=vmin, vmax=vmax)
 divider = make_axes_locatable(ax[0])
 cax = divider.append_axes("right", size="5%", pad=0.1)
 cbar = plt.colorbar(im, cax=cax)
 cbar.ax.tick_params(labelsize=10)
 
-# Normalized
-im = ax[1].imshow(Sigma_norm, cmap="viridis", vmin=vmin, vmax=vmax)
+# Difference
[…]

### 2020-11-29 tex/figures/periodic_error_asymptotic.py

@@ -1,0 +1,108 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import george
+from george.kernels import CosineKernel
+from scipy.linalg import cho_factor
+from tqdm import tqdm
+
+
+def norm_cov(mu, Sig, N=20):
+
+    # Terms
+    K = Sig.shape[0]
+    j = np.ones((K, 1))
+    m = np.mean(Sig)
+    mvec = (Sig @ j) / K
+    z = m / mu ** 2
+    s = m * j - mvec
+
+    # Coefficients
+    fac = 1.0
+    alpha = 0.0
+    beta = 0.0
+    for n in range(0, N + 1):
+        alpha += fac
+        beta += 2 * n * fac
+        fac *= z * (2 * n + 3)
+
+    # Record the value of the expansion parameter
+    print("z:", z)
+
+    # We're done
+    return (
+        (alpha / mu ** 2) * Sig
+        + (alpha / (mu ** 2 * m)) * (s @ s.T - mvec @ mvec.T)
+        + (beta / (mu ** 2 * m)) * (s @ s.T)
+    )
+
+
+# GP Mean
+mu = 0.75
+
+# GP Amplitude
+std = 0.1
+
+# Asymmetry term
+offset = 0.5
+
+# Dimension
+K = 10
+
+# Expansion order in our series solution
+N = 20
+
+# Get the covariance matrix
+t = np.linspace(0, 1, K)
+period = 0.75
+kernel = std ** 2 * (offset + CosineKernel(np.log(period)))
+gp = george.GP(kernel)
+gp.compute(t)
+Sigma = gp.get_matrix(t) + 1e-12 * np.eye(K)
+
+# Compute the normalized covariance using the series expansion
+Sigma_norm = norm_cov(mu, Sigma, N=N)
+
+# Compute it numerically by sampling
+np.random.seed(0)
+L = np.tril(cho_factor(Sigma, lower=True)[0])
+
+
+ntrials = 30
+log10M = np.linspace(2, 6, 24)
+M = np.array(10 ** log10M, dtype=int)
+
+error_max = np.zeros((ntrials, len(M)))
+error_med = np.zeros((ntrials, len(M)))
+
+for n in tqdm(range(ntrials)):
+    for k in range(len(M)):
+        np.random.seed(n)
+        u = np.random.randn(K, M[k])
+        x = mu + L @ u
[…]

### 2020-11-30 tex/ms.tex
better notation

@@
 process can be well \emph{approximated} by a GP, albeit one with a different
-covariance matrix $\tilde{\pmb{\Sigma}}$ that is not simply a scalar
+covariance matrix $\btilde{\pmb{\Sigma}}$ that is not simply a scalar
 multiple of the original covariance matrix. Moreover, if the original process
@@
 
-Let $\mathbf{x} = \left( x_0 \,\, \cdots \,\, x_{K-1} \right)^\top$
+Let $\mathbbb{x} = \left( \mathbb{x}_0 \,\, \cdots \,\, \mathbb{x}_{K-1} \right)^\top$
 be a $K$-dimensional multivariate normal random variable distributed
@@
 \begin{align}
-    \mathbf{x} \sim \mathcal{N}\left( \pmb{\mu}, \pmb{\Sigma} \right)
+    \mathbbb{x} \sim \mathcal{N}\left( \pmb{\mu}, \pmb{\Sigma} \right)
     \quad.
@@
 %
-Now suppose we cannot observe samples of $\mathbf{x}$ directly, but instead we can
+Now suppose we cannot observe samples of $\mathbbb{x}$ directly, but instead we can
 observe samples from the \emph{normalized} process, which we will call
-$\tilde{\mathbf{x}}$:
+$\btilde{\mathbbb{x}}$:
 %
 \begin{align}
-    \tilde{\mathbf{x}}
-     & \equiv \frac{\mathbf{x}}{\bar{x}}
+    \btilde{\mathbbb{x}}
+     & \equiv \frac{\mathbbb{x}}{\bbar{\mathbb{x}}}
     \nonumber                                                              \\[0.5em]
-     & = \frac{\mathbf{x}}{\frac{1}{K}\sum\limits_{k=0}^{K-1} x}
+     & = \frac{\mathbbb{x}}{\frac{1}{K}\sum\limits_{k=0}^{K-1} \mathbb{x}}
     \quad.
@@
 %
-The random variable $\tilde{\mathbf{x}}$ is no longer normally distributed, but as long as
-the variance of $\bar{x}$ is small, we can attempt to approximate it as such. Let the mean
-and covariance of $\tilde{\mathbf{x}}$ be $\tilde{\pmb{\mu}}$ and $\tilde{\pmb{\Sigma}}$, respectively:
+The random variable $\btilde{\mathbbb{x}}$ is no longer normally distributed, but as long as
+the variance of $\bbar{\mathbb{x}}$ is small, we can attempt to approximate it as such. Let the mean
+and covariance of $\btilde{\mathbbb{x}}$ be $\btilde{\pmb{\mu}}$ and $\btilde{\pmb{\Sigma}}$, respectively:
 %
 \begin{align}
-    \tilde{\mathbf{x}} \mathrel{\dot\sim} \mathcal{N}\left( \tilde{\pmb{\mu}}, \tilde{\pmb{\Sigma}} \right)
+    \btilde{\mathbbb{x}} \mathrel{\dot\sim} \mathcal{N}\left( \btilde{\pmb{\mu}}, \btilde{\pmb{\Sigma}} \right)
     \quad.
@@
 \begin{align}
-    \tilde{\pmb{\mu}} = \mathbf{j}
+    \btilde{\pmb{\mu}} = \mathbf{j}
     \quad.
@@
 %
-What is the expression for $\tilde{\pmb{\Sigma}}$?
+What is the expression for $\btilde{\pmb{\Sigma}}$?
 
@@
 \begin{align}
-    \tilde{\pmb{\Sigma}}
+    \btilde{\pmb{\Sigma}}
      & =
-    \mathbb{E}\big[ (\tilde{\mathbf{x}} - \tilde{\pmb{\mu}}) (\tilde{\mathbf{x}} - \tilde{\pmb{\mu}} )^\top \big]
+    \mathbbb{E}\big[ (\btilde{\mathbbb{x}} - \btilde{\pmb{\mu}}) (\btilde{\mathbbb{x}} - \btilde{\pmb{\mu}} )^\top \big]
     \nonumber \\[0.5em]
      & =
-    \mathbb{E}\left[
-        \left(\frac{\mathbf{x}}{\bar{x}} - \mathbf{j}\right)
-        \left(\frac{\mathbf{x}}{\bar{x}} - \mathbf{j}\right)^\top
+    \mathbbb{E}\left[
+        \left(\frac{\mathbbb{x}}{\bbar{\mathbb{x}}} - \mathbf{j}\right)
+        \left(\frac{\mathbbb{x}}{\bbar{\mathbb{x}}} - \mathbf{j}\right)^\top
         \right]
@@
      & =
-    \mathbb{E}\left[
-        \frac{\mathbf{x}\mathbf{x}^\top}{\bar{x}^2}
+    \mathbbb{E}\left[
+        \frac{\mathbbb{x}\mathbbb{x}^\top}{\bbar{\mathbb{x}}^2}
         -
-        \frac{\mathbf{x}\,\mathbf{j}^\top}{\bar{x}}
+        \frac{\mathbbb{x}\,\mathbf{j}^\top}{\bbar{\mathbb{x}}}
         -
-        \frac{\mathbf{j}\,\mathbf{x}^\top}{\bar{x}}
+        \frac{\mathbf{j}\,\mathbbb{x}^\top}{\bbar{\mathbb{x}}}
         +
@@
      & =
-    \mathbb{E}\left[
-        \frac{\mathbf{x}\mathbf{x}^\top}{\bar{x}^2}
+    \mathbbb{E}\left[
+        \frac{\mathbbb{x}\mathbbb{x}^\top}{\bbar{\mathbb{x}}^2}
         \right]
     -
-    \mathbb{E}\left[
-        \frac{\mathbf{x}\,\mathbf{j}^\top}{\bar{x}}
+    \mathbbb{E}\left[
+        \frac{\mathbbb{x}\,\mathbf{j}^\top}{\bbar{\mathbb{x}}}
         \right]
     -
-    \mathbb{E}\left[
-        \frac{\mathbf{j}\,\mathbf{x}^\top}{\bar{x}}
+    \mathbbb{E}\left[
+        \frac{\mathbf{j}\,\mathbbb{x}^\top}{\bbar{\mathbb{x}}}
         \right]
@@
 \begin{align}
-    \mathbf{x} = \pmb{\mu} + \mathbf{L} \mathbf{u}
+    \mathbbb{x} = \pmb{\mu} + \mathbf{L} \mathbbb{u}
     \quad,
@@
 %
-and $\mathbf{u}$ is a standard multivariate normal random variable,
+and $\mathbbb{u}$ is a standard multivariate normal random variable,
 %
 \begin{align}
-    \mathbf{u} \sim \mathcal{N}\left( 0, \mathbf{I} \right)
+    \mathbbb{u} \sim \mathcal{N}\left( 0, \mathbf{I} \right)
     \quad,
@@
 $K \times K$ identity matrix.
-The expression for the covariance $\tilde{\pmb{\Sigma}}$ may now be written
+The expression for the covariance $\btilde{\pmb{\Sigma}}$ may now be written
 %
@@
     \label{eq:SigmaTildeExp}
-    \tilde{\pmb{\Sigma}}
+    \btilde{\pmb{\Sigma}}
      & =
-    \mathbb{E}\left[
+    \mathbbb{E}\left[
         \frac{
-            (\pmb{\mu} + \mathbf{L} \mathbf{u})(\pmb{\mu} + \mathbf{L} \mathbf{u})^\top
+            (\pmb{\mu} + \mathbf{L} \mathbbb{u})(\pmb{\mu} + \mathbf{L} \mathbbb{u})^\top
         }{
-            \bar{x}^2
+            \bbar{\mathbb{x}}^2
         }
@@
     -
-    \mathbb{E}\left[
+    \mathbbb{E}\left[
         \frac{
-            (\pmb{\mu} + \mathbf{L} \mathbf{u})\mathbf{j}^\top
+            (\pmb{\mu} + \mathbf{L} \mathbbb{u})\mathbf{j}^\top
         }{
-            \bar{x}
+            \bbar{\mathbb{x}}
         }
@@
     -
-    \mathbb{E}\left[
+    \mathbbb{E}\left[
         \frac{
-            \mathbf{j}(\pmb{\mu} + \mathbf{L} \mathbf{u})^\top
+            \mathbf{j}(\pmb{\mu} + \mathbf{L} \mathbbb{u})^\top
         }{
-            \bar{x}
+            \bbar{\mathbb{x}}
         }
@@
 %
-The mean $\bar{x}$ is
+The mean $\bbar{\mathbb{x}}$ is
 %
 \begin{align}
-    \bar{x} & = \sum\limits_{j=0}^{K-1}(\mu_j + L_{i,j}u_j)
+    \bbar{\mathbb{x}} & = \sum\limits_{j=0}^{K-1}(\mu_j + L_{ij} \mathbb{u}_j)
     \nonumber                                                                  \\
                       & =
-    \mu + \frac{1}{K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}
+    \mu + \frac{1}{K}\mathbf{j}^\top \mathbf{L} \, \mathbbb{u}
     \nonumber                                                                  \\
-            & = \mu(1 + \epsilon)
+                      & = \mu(1 + \mathbb{r})
     \quad,
@@
     \label{eq:epsilon}
-    \epsilon
-     & \equiv \frac{\bar{x}}{\mu} - 1
+    \mathbb{r}
+     & \equiv \frac{\bbar{\mathbb{x}}}{\mu} - 1
     \nonumber                                                     \\[0.5em]
-     & = \frac{1}{\mu K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}
+     & = \frac{1}{\mu K}\mathbf{j}^\top \mathbf{L} \, \mathbbb{u}
     \quad.
@@
     \label{eq:SigmaPQR}
-    \tilde{\pmb{\Sigma}}
+    \btilde{\pmb{\Sigma}}
      & =
@@
     \mathbf{P} & \equiv
-    \mathbb{E}\Big[
-        \frac{\epsilon^2 \, \mathbf{j} \, \mathbf{j}^\top}{(1 + \epsilon)^2}
+    \mathbbb{E}\Big[
+        \frac{\mathbb{r}^2 \, \mathbf{j} \, \mathbf{j}^\top}{(1 + \mathbb{r})^2}
         \Big]
@@
     \mathbf{Q} & \equiv
-    \mathbb{E}\left[
-        \frac{\epsilon\, \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top}{(1 + \epsilon)^2}
+    \mathbbb{E}\left[
+        \frac{\mathbb{r}\, \mathbf{L} \, \mathbbb{u} \, \mathbf{j}^\top}{(1 + \mathbb{r})^2}
         \right]
@@
     \mathbf{R} & \equiv
-    \mathbb{E}\left[
-        \frac{ \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top}{(1 + \epsilon)^2}
+    \mathbbb{E}\left[
+        \frac{ \mathbf{L} \, \mathbbb{u} \, \mathbbb{u}^\top \, \mathbf{L}^\top}{(1 + \mathbb{r})^2}
         \right]
@@
 intractable. Provided
-$\big|\epsilon| < 1$ (an assumption we'll revisit below), we can Taylor expand the matrices as
+$\big|\mathbb{r}| < 1$ (an assumption we'll revisit below), we can Taylor expand the matrices as
 %
@@
     \,
-    \mathbb{E}\left[
-        \epsilon^{n + 2}
+    \mathbbb{E}\left[
+        \mathbb{r}^{n + 2}
         \,
@@
     \,
-    \mathbb{E}\left[
-        \epsilon^{n + 1} \,
+    \mathbbb{E}\left[
+        \mathbb{r}^{n + 1} \,
         \mathbf{L}
         \,
-        \mathbf{u}
+        \mathbbb{u}
         \,
@@
     \,
-    \mathbb{E}\left[
-        \epsilon^n \, \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top
+    \mathbbb{E}\left[
+        \mathbb{r}^n \, \mathbf{L} \, \mathbbb{u} \, \mathbbb{u}^\top \mathbf{L}^\top
         \right]
@@
 \begin{align}
-    \mathbb{E}\left[
-        \epsilon^{n + 2} \, \mathbf{j} \, \mathbf{j}^\top
+    \mathbbb{E}\left[
+        \mathbb{r}^{n + 2} \, \mathbf{j} \, \mathbf{j}^\top
         \right]
@@
     \\[0.5em]
-    \mathbb{E}\left[
-        \epsilon^{n + 1} \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top
+    \mathbbb{E}\left[
+        \mathbb{r}^{n + 1} \, \mathbf{L} \, \mathbbb{u} \, \mathbf{j}^\top
         \right]
@@
     \\[0.5em]
-    \mathbb{E}\left[
-        \epsilon^n \, \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top
+    \mathbbb{E}\left[
+        \mathbb{r}^n \, \mathbf{L} \, \mathbbb{u} \, \mathbbb{u}^\top \mathbf{L}^\top
         \right]
@@
     \label{eq:SigmaTilde}
-    \tilde{\pmb{\Sigma}}
+    \btilde{\pmb{\Sigma}}
      & =
@@
 and (\ref{eq:WhereItAllGoesWrong3}): the Taylor expansion converges only for
-$\big|\epsilon| < 1$. The quantity $\epsilon$ (Equation~\ref{eq:epsilon})
-is indeed small provided the sample mean $\bar{x}$ is close to the GP
-mean $\mu$. However, $\epsilon$ is a random variable, equal to
+$\big|\mathbb{r}| < 1$. The quantity $\mathbb{r}$ (Equation~\ref{eq:epsilon})
+is indeed small provided the sample mean $\bbar{\mathbb{x}}$ is close to the GP
+mean $\mu$. However, $\mathbb{r}$ is a random variable, equal to
 the weighted sum of $K$ standard normal random variables. Because a normal
-distribution has infinite support, $\epsilon$ is guaranteed to take on
+distribution has infinite support, $\mathbb{r}$ is guaranteed to take on
 values greater than unity in the limit that an infinite number of samples
@@
             between the series solution and the numerical solution,
-            normalized to the largest element in $\pmb{\tilde{\Sigma}}$.
+            normalized to the largest element in $\btilde{\pmb{\Sigma}}$.
             The maximum difference between the two solutions is less

### 2020-11-30 tex/ms.tex
better notation

@@
 
-\section{The problem}
+\section{Normalized Gaussian Processes}
+\label{sec:main}
+
+\subsection{Notation}
+\label{sec:notation}
+
+We adopt
+the following conventions throughout this paper:
+scalars are represented by italic lowercase letters (i.e., $x$)
+and occasionally upercase letters, in particular if the value
+corresponds to an integer (i.e., $K$);
+column vectors are
+represented by boldface lowercase letters
+($\mathbf{x}$); and matrices and other linear operators are represented
+by boldface capital letters ($\mathbf{X}$).
+To make the distinction between numerical values and random variables as
+clear as possible, we use blackboard fonts to denote random variables
+(i.e., $\mathbb{x}$ for a scalar random variable and $\mathbbb{x}$
+for a vector-valued random variable).
+Finally, we use a bar symbol
+($\bbar{\mathbb{x}}$) to denote the mean of a vector-valued random
+variable and the tilde symbol
+($\btilde{\mathbf{x}}$ or $\btilde{\mathbbb{x}}$) to denote a numerical
+quantity or random variable corresponding
+to a normalized Gaussian process.
+
+%
+
+\subsection{The problem}
+\label{sec:problem}
 
@@
 \begin{align}
-    \pmb{\mu} = \mu \, \mathbf{j}
+    \pmb{\mu} = \mu \, \mathbf{1}
 \end{align}
 %
-where $\mathbf{j}$ is the vector of $K$ ones.
+where $\mathbf{1}$ is the vector of $K$ ones.
 %
@@
 \begin{align}
-    \btilde{\pmb{\mu}} = \mathbf{j}
+    \btilde{\pmb{\mu}} = \mathbf{1}
     \quad.
@@
 
-\section{The solution}
+\subsection{The solution}
+\label{sec:solution}
 
-The covariance is given by
+From the definition of the covariance, we may compute $\btilde{\pmb{\Sigma}}$ from
 %
@@
     \mathbbb{E}\left[
-        \left(\frac{\mathbbb{x}}{\bbar{\mathbb{x}}} - \mathbf{j}\right)
-        \left(\frac{\mathbbb{x}}{\bbar{\mathbb{x}}} - \mathbf{j}\right)^\top
+        \left(\frac{\mathbbb{x}}{\bbar{\mathbb{x}}} - \mathbf{1}\right)
+        \left(\frac{\mathbbb{x}}{\bbar{\mathbb{x}}} - \mathbf{1}\right)^\top
         \right]
@@
         -
-        \frac{\mathbbb{x}\,\mathbf{j}^\top}{\bbar{\mathbb{x}}}
+        \frac{\mathbbb{x}\,\mathbf{1}^\top}{\bbar{\mathbb{x}}}
         -
-        \frac{\mathbf{j}\,\mathbbb{x}^\top}{\bbar{\mathbb{x}}}
+        \frac{\mathbf{1}\,\mathbbb{x}^\top}{\bbar{\mathbb{x}}}
         +
-        \mathbf{j} \, \mathbf{j}^\top
+        \mathbf{1} \, \mathbf{1}^\top
         \right]
@@
     \mathbbb{E}\left[
-        \frac{\mathbbb{x}\,\mathbf{j}^\top}{\bbar{\mathbb{x}}}
+        \frac{\mathbbb{x}\,\mathbf{1}^\top}{\bbar{\mathbb{x}}}
         \right]
@@
     \mathbbb{E}\left[
-        \frac{\mathbf{j}\,\mathbbb{x}^\top}{\bbar{\mathbb{x}}}
+        \frac{\mathbf{1}\,\mathbbb{x}^\top}{\bbar{\mathbb{x}}}
         \right]
     +
-    \mathbf{j} \, \mathbf{j}^\top
-    \quad.
+    \mathbf{1} \, \mathbf{1}^\top
+    \quad,
 \end{align}
 %
-To evaluate this, it is convenient to write
+where $\mathbbb{E}\left[ \cdots \right]$ denotes the expected value of a random variable.
+%
+To evaluate the expression above, it is convenient to write
 %
@@
 \begin{align}
-    \mathbbb{u} \sim \mathcal{N}\left( 0, \mathbf{I} \right)
+    \mathbbb{u} \sim \mathcal{N}\left( \mathbf{0}, \mathbf{I} \right)
     \quad,
@@
         \frac{
-            (\pmb{\mu} + \mathbf{L} \mathbbb{u})\mathbf{j}^\top
+            (\pmb{\mu} + \mathbf{L} \mathbbb{u})\mathbf{1}^\top
         }{
@@
         \frac{
-            \mathbf{j}(\pmb{\mu} + \mathbf{L} \mathbbb{u})^\top
+            \mathbf{1}(\pmb{\mu} + \mathbf{L} \mathbbb{u})^\top
         }{
@@
     +
-    \mathbf{j} \, \mathbf{j}^\top
+    \mathbf{1} \, \mathbf{1}^\top
 \end{align}
@@
                       & =
-    \mu + \frac{1}{K}\mathbf{j}^\top \mathbf{L} \, \mathbbb{u}
+    \mu + \frac{1}{K}\mathbf{1}^\top \mathbf{L} \, \mathbbb{u}
     \nonumber                                                                  \\
@@
     \nonumber                                                     \\[0.5em]
-     & = \frac{1}{\mu K}\mathbf{j}^\top \mathbf{L} \, \mathbbb{u}
+     & = \frac{1}{\mu K}\mathbf{1}^\top \mathbf{L} \, \mathbbb{u}
     \quad.
@@
     \mathbbb{E}\Big[
-        \frac{\mathbb{r}^2 \, \mathbf{j} \, \mathbf{j}^\top}{(1 + \mathbb{r})^2}
+        \frac{\mathbb{r}^2 \, \mathbf{1} \, \mathbf{1}^\top}{(1 + \mathbb{r})^2}
         \Big]
@@
     \mathbbb{E}\left[
-        \frac{\mathbb{r}\, \mathbf{L} \, \mathbbb{u} \, \mathbf{j}^\top}{(1 + \mathbb{r})^2}
+        \frac{\mathbb{r}\, \mathbf{L} \, \mathbbb{u} \, \mathbf{1}^\top}{(1 + \mathbb{r})^2}
         \right]
@@
         \,
-        \mathbf{j} \, \mathbf{j}^\top
+        \mathbf{1} \, \mathbf{1}^\top
         \right]
@@
         \,
-        \mathbf{j}^\top
+        \mathbf{1}^\top
         \right]
@@
     \mathbbb{E}\left[
-        \mathbb{r}^{n + 2} \, \mathbf{j} \, \mathbf{j}^\top
+        \mathbb{r}^{n + 2} \, \mathbf{1} \, \mathbf{1}^\top
         \right]
      & =
-    \frac{(n + 1) g_{n} m^\frac{n+2}{2}}{\mu^{n+2}} \, \mathbf{j} \, \mathbf{j}^\top
+    \frac{(n + 1) g_{n} m^\frac{n+2}{2}}{\mu^{n+2}} \, \mathbf{1} \, \mathbf{1}^\top
     \\[0.5em]
     \mathbbb{E}\left[
-        \mathbb{r}^{n + 1} \, \mathbf{L} \, \mathbbb{u} \, \mathbf{j}^\top
+        \mathbb{r}^{n + 1} \, \mathbf{L} \, \mathbbb{u} \, \mathbf{1}^\top
         \right]
      & =
-    \frac{(n + 1) K \, g_{n} m^\frac{n}{2}}{\mu^{n+1}} \, \mathbf{m} \, \mathbf{j}^\top
+    \frac{(n + 1) K \, g_{n} m^\frac{n+2}{2}}{\mu^{n+1}} \, \mathbf{q} \, \mathbf{1}^\top
     \\[0.5em]
@@
     \frac{g_n}{\mu^n} \left(
-    n \,  m^\frac{n - 2}{2} \mathbf{m} \, \mathbf{m}^\top + m^\frac{n}{2} \pmb{\Sigma}
+    n \,  m^\frac{n + 2}{2} \mathbf{q} \, \mathbf{q}^\top + m^\frac{n}{2} \pmb{\Sigma}
     \right)
@@
 \begin{align}
-    \mathbf{m}
+    m
      & \equiv
-    \frac{1}{K} \pmb{\Sigma} \, \mathbf{j}
+    \frac{1}{K^2} \mathbf{1}^\top \pmb{\Sigma} \, \mathbf{1}
 \end{align}
 %
-is the average of each row in $\pmb{\Sigma}$, and
+is the average of all elements in $\pmb{\Sigma}$, and
 %
 \begin{align}
-    m
+    \mathbf{q}
      & \equiv
-    \frac{1}{K^2} \mathbf{j}^\top \pmb{\Sigma} \, \mathbf{j}
+    \frac{1}{K m} \pmb{\Sigma} \, \mathbf{1}
 \end{align}
 %
-is the average of all elements in $\pmb{\Sigma}$.
+is the ratio of the average of each row in $\pmb{\Sigma}$ to the average of
+all elements in $\pmb{\Sigma}$.
+
 %
@@
      & =
-    \frac{\alpha \, \pmb{\Sigma}}{\mu^2}  +
-    \frac{\alpha \, \left(\mathbf{s} \, \mathbf{s}^\top - \mathbf{m} \, \mathbf{m}^\top\right)}{\mu^2 m}  +
-    \frac{\beta \, \left(\mathbf{s} \, \mathbf{s}^\top\right)}{\mu^2 m}
+    \frac{\alpha}{\mu^2} \pmb{\Sigma} +
+    z \Big(
+    (\alpha + \beta) \, \mathbf{p} \, \mathbf{p}^\top
+    - \alpha \, \mathbf{q} \, \mathbf{q}^\top
+    \Big)
     \quad,
@@
 \begin{align}
-    \mathbf{s}
+    \mathbf{p}
      & \equiv
-    m \, \mathbf{j} - \mathbf{m}
+    \mathbf{1} - \mathbf{q}
     \\[1em]
@@
 
-\section{The Bad News}
+\subsection{The Bad News}
+\label{sec:badnews}
 %
@@
 
+%
+\begin{figure}[t!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/alpha_beta_values.pdf}
+        \oscaption{alpha_beta_values}{%
+            Caption.
+            \label{fig:alpha_beta_values}
+        }
+    \end{centering}
+\end{figure}
+%
+
 \section{Non-stationarity}

### 2020-11-30 tex/figures/alpha_beta_values.py

@@ -1,0 +1,58 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from tqdm import tqdm
+
+
+def alpha_beta(z, nmax=50):
+
+    fac_prev = 1.0
+    fac = 1.0
+    alpha = 0.0
+    beta = 0.0
+    for n in range(0, nmax + 1):
+        if fac > fac_prev:
+            break
+        alpha += fac
+        beta += 2 * n * fac
+        fac_prev = fac
+        fac *= z * (2 * n + 3)
+
+    return alpha, beta, fac, 2 * n * fac
+
+
+zmax = 0.1
+
+z = np.logspace(-5, np.log10(zmax), 1000)
+alpha = np.zeros_like(z)
+beta = np.zeros_like(z)
+error1 = np.zeros_like(z)
+error2 = np.zeros_like(z)
+for k in range(len(z)):
+    alpha[k], beta[k], error1[k], error2[k] = alpha_beta(z[k])
+
+fig, ax = plt.subplots(1)
+axt = ax.twinx()
+ax.plot(z, alpha, color="C0", label=r"$\alpha$")
+axt.plot(z, beta, color="C1")
+
+ax.fill_between(z, alpha - error1, alpha + error1, color="C0", alpha=0.1)
+axt.fill_between(z, beta - error2, beta + error2, color="C1", alpha=0.1)
+
+ax.set_xscale("log")
+
+ax.set_ylim(0.95, 2)
+axt.set_ylim(-0.1, 2)
+
+ax.set_xlabel(r"$z$", fontsize=26)
+ax.set_ylabel(r"$\alpha$", fontsize=26)
+axt.set_ylabel(r"$\beta$", fontsize=26)
+
+ax.plot(z, alpha * np.nan, color="C1", label=r"$\beta$")
+ax.legend(loc="upper left")
+
+
+ax.axvline(0.023, color="k", ls="--", lw=1, alpha=0.75)
+
+
+# We're done
+fig.savefig(__file__.replace(".py", ".pdf"), bbox_inches="tight")
